---
title: "101_Select_data"
author: "DHJ"
date: "5 5 2020"
output: html_document
---

## 1. Libraries
```{r}

library(readr)
library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(safejoin)   # github moodymudskipper

library(maps)
# install.packages("mapdata")
library(mapdata)

simple_map <- map_data("worldHires", "Norway")

```


## 2. Data  

### Main data
```{r}

dat_old <- readRDS("../Milkys/Data/10_data_all.RData") %>%
  filter(MYEAR >= 1994)

# "Input_data/"
dat <- readRDS("Input_data/109_adjusted_data_2020-08-05.rds") %>%
  filter(MYEAR >= 1994)

names(dat)
names(dat_old)

xtabs(~MYEAR, dat)

```
### Some tables  
```{r}

cat("---------------------------------------------------------------- \n")
cat("PARAMETERS \n")
dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005) %>%
  xtabs(~PARAM + MYEAR, .)

cat("---------------------------------------------------------------- \n")
cat("STATIONS \n")
cat("Urban ones: 24B = Bergen, 43B2 = Tromsø harbour, 30B = Oslo \n")
dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005) %>%
  xtabs(~STATION_CODE + MYEAR, .)


if (FALSE){
  dat %>%
    filter(STATION_CODE %in% "24B" & MYEAR >= 2005) %>%
    xtabs(~PARAM + MYEAR, .)
  
  # Ålesund: no PFAS analysed
  dat %>%
    filter(STATION_CODE %in% "28B" & MYEAR >= 2005) %>%
    xtabs(~PARAM + MYEAR, .)
}

```

### Coordinates  
```{r}

col_spec <- cols(
  .default = col_double(),
  ICES_ecoregion = col_character(),
  OSPAR_subregion = col_character(),
  OSPAR_shore = col_character(),
  Country = col_character(),
  Country_ISO = col_character(),
  Organisation = col_character(),
  Station_Name = col_character(),
  ReplacedBy = col_character(),
  MSTAT = col_character(),  Other_area = col_logical(),
  WLTYP = col_character(),
  Geometry = col_character(),
  All_Data_Types = col_character(),
  All_Biota_Types = col_character(),
  All_Sediment_Types = col_character(),
  All_Water_Types = col_character(),
  Notes = col_character()
)

df_stations <- readr::read_tsv("C:/Data/seksjon 212/MIME-dhj/OSPAR_MIME_2019/StationDictionary_20191104/StationDictionary_20191104_utf8.txt",
                               col_types = col_spec) %>%
  filter(Country == "Norway") %>% 
  mutate(STATION_CODE = stringr::str_extract(Station_Name, "([^[[:blank:]]]+)"))  # Extract the code


```


## 3. Pick stations by abundance   

### Stations  
Number of years during the last 10 years  
```{r}

df <- dat %>% 
  filter(MYEAR >= 2009) %>%
  distinct(STATION_CODE, MYEAR) %>%
  count(STATION_CODE) %>%
  arrange(desc(n))

df 

```

### Pick stations with >= 4 of the last 10 years  
```{r}

stations <- df %>%
  filter(n >= 4) %>%
  pull(STATION_CODE)

# Snail stations 
sel <- grepl("G", stations)
# stations[sel]

stations <- stations[!sel]
stations %>% sort()

```



## 4. Check stations


### Check if we have them in the station dictionary  
```{r}

sel <- stations %in% df_stations$STATION_CODE
mean(sel)  # 1 yes we have

```

### Fix MSTAT for our purpose  
```{r}

if (FALSE){
  df_stations %>%
    filter(STATION_CODE %in% stations) %>% 
    select(Station_Name:MSTAT, Lon, Lat) %>%
    arrange(MSTAT) %>%
    View()
}

df_stations <- df_stations %>%
  mutate(MSTAT = case_when(
    grepl("13B", Station_Name) ~ "IH",
    grepl("I969", Station_Name) ~ "IH",
    grepl("53F", Station_Name) ~ "IH",
    TRUE ~ MSTAT
  ))

```

### Interactive map
```{r}

library(leaflet)

lookup_colors <- tibble(
  MSTAT = c("B", "RH", "IH"),
  color = c("blue", "green", "red")
)

df <- df_stations %>%
  filter(STATION_CODE %in% stations) %>%
  left_join(lookup_colors)

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = df$color
  )

leaflet(df) %>%
  addTiles() %>%
  addAwesomeMarkers(~Lon, ~Lat, icon=icons, label=~as.character(Station_Name))

```





### Test map of stations
```{r}

gg <- df_stations %>%
  filter(STATION_CODE %in% stations) %>% 
  mutate(Impacted = (MSTAT %in% "IH")) %>%
  ggplot(aes(Lon, Lat, color = MSTAT)) +
  scale_color_manual(values = c("blue4", "red", "green3")) +
  annotation_map(simple_map, fill = "grey20") +
  geom_point()

gg +
  coord_map("lambert", parameters = c(10.4, 59.3)) +
  facet_grid(cols = vars(Impacted))

# Southern
gg +
  coord_map("lambert", parameters = c(10.4, 59.3), xlim = c(4,12), ylim = c(58, 62)) +
  facet_grid(cols = vars(Impacted))
  
# Detail: Oslofjorden
gg +
  coord_map("lambert", parameters = c(10.4, 59.3), xlim = c(8,12), ylim = c(58, 60)) +
  facet_grid(cols = vars(Impacted))

# Detail: Sørfjorden og Bømlo
gg +
  coord_map("lambert", parameters = c(10.4, 59.3), xlim = c(5,7), ylim = c(59.3, 60.5)) +
  facet_grid(cols = vars(Impacted))

# Mid
gg +
  coord_map("lambert", parameters = c(10.4, 59.3), xlim = c(4,12), ylim = c(61.5, 64.5)) +
  facet_grid(cols = vars(Impacted))
  
# Nordland
gg +
  coord_map("lambert", parameters = c(10.4, 59.3), xlim = c(10, 18), ylim = c(64, 68)) +
  facet_grid(cols = vars(Impacted))
  
# Detail: Ranfjorden
gg +
  coord_map("lambert", parameters = c(10.4, 59.3), xlim = c(12,14.5), ylim = c(66, 66.5)) +
  facet_grid(cols = vars(Impacted))
  
# Troms og Finnmark
gg +
  coord_map("lambert", parameters = c(10.4, 59.3), xlim = c(16,31), ylim = c(68, 72)) +
  facet_grid(cols = vars(Impacted))
  
  

```



## 5. Pick parameters  
Number of station-years during the last 10 years  
```{r}

df <- dat %>% 
  filter(MYEAR >= 2009 & STATION_CODE %in% stations) %>%
  distinct(PARAM, STATION_CODE, MYEAR) %>%
  count(PARAM) %>%
  arrange(desc(n))

df 

```

### Pick parameters by editing sorted list   
```{r}

params <- df %>%
  filter(n >= 30) %>%
  pull(PARAM) %>%
  sort()

# dput(params)

if (FALSE){

    params <- c(
    "AG", "AS", "CD", "CO", "CR", "CU", "HG", "SN", 
    "NI", "PB", "ZN",
    "4-T-NP", 
    "BDE100", "BDE28", "BDE47", "BDE6S", "BDE99", "CB_S7", 
    "CB101", "CB105", "CB118", "CB123", "CB126", "CB138", "CB153", "CB156", "CB157", 
    "CB167", "CB169", "CB180", "CB28", "CB52", "CB77", 
    "DDEPP", "DDTEP", 
    "HBCDA", "HBCDB", "HBCDD", "HBCDG", 
    "HCB", "HCHA", "HCHG", 
    "MCCP", "QCB", "SCCP", "TBBPA", "TDEPP",
    "PFOS",
    "Delta13C", "Delta15N"
  )
  
}

```


## 6. Add isotopes   
Not so easy because of pooled liver samples. Do later!  
```{r}

if (FALSE){
  
  supp_params <- c("Delta13C", "Delta15N")
  
  dat_for_join <- dat %>%
    filter(STATION_CODE %in% stations & PARAM %in% supp_params) %>%
    select(MYEAR:SAMPLE_NO2, PARAM, VALUE_WW) %>%
    pivot_wider(names_from = PARAM, values_from = VALUE_WW)
  
  dat2 <- dat %>%
    safe_left_join(dat_for_join, check = "V", 
                   by = c("MYEAR", "STATION_CODE", "LATIN_NAME", "SAMPLE_NO2"))
  
}

```

## 7. Save data  
```{r}

dat %>%
  filter(STATION_CODE %in% stations & PARAM %in% params) %>%
  saveRDS("Data/101_Selected_data.rds")

df_stations %>%
  filter(STATION_CODE %in% stations) %>%
  saveRDS("Data/101_Selected_stations.rds")


```


