---
title: "103_Distance_along_coast"
author: "DHJ"
date: "12 5 2020"
output:
  html_document:
    toc: true    
    toc_float: true
    keep_md: true  
---


## 1. Packages + definitions  
```{r, warning=FALSE, message=FALSE, results='hide'}

library(ggplot2)
library(dplyr)
library(purrr)
library(sp)

crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"

```

Functions  
```{r}
source("103_Distance_along_coast_functions.R")

```


## 2. Data

### Station data  
```{r}

df_stations <- readRDS("Data/101_Selected_stations.rds")

```

### Add stations

```{r}

df_stations_extra <- read.csv(textConnection("
STATION_CODE, Station_Name, Lat, Lon, MSTAT,
24B, 24B Bergen harbour, 60.39664, 5.27069, IH
36A1, 36A1 Færder, 59.07357, 10.42522, RH
28A2, 28A2 Vågsvåg, 61.93622,  5.048783333, RH
97A3, 97A3 Bodø harbour, 67.2963, 14.3956, IH
I714, I714 Sylterøya (Langesundfjord), 59.0514, 9.7038, IH
"),
stringsAsFactors = FALSE
)
  
df_stations <- df_stations %>%
  bind_rows(df_stations_extra)

```

### Coordinates along the coastal current  
Made in script 102  
```{r}
coast <- readRDS("Data/102_coast_coordinates.rmd")

```

### Norway map data
```{r}
#
# Get Norway map data
#
test <- maps::map("world", "Norway", plot = FALSE)   # map data for Norway - this is just to get region names
sel <- grepl("Svalbard", test$names) | test$names == "Norway:Jan Mayen"  # select Svalbard + Jan Mayen
# test$names[!sel]
map <- maps::map("world", test$names[!sel], exact = TRUE, plot = FALSE)  # Norway w/o Svalbard + Jan Mayen
map_df <- data.frame(Longitude = map$x, Latitude = map$y)

```


### Plot coordinates along coast  
Long-lat coordinates  
```{r}

ggplot(map_df, aes(Longitude, Latitude)) + 
  geom_path() +
  coord_map("lambert", lat0 = 64, lon0 = 11) +
  geom_path(data = coast, color = "blue") +
  geom_point(data = coast, color = "blue") 

```


## 4. Add UTM coordinates (x and y) to map
```{r}
#
# Add UTM coordinates (x and y) to map
#
coordinate_exists <- !is.na(map_df$Longitude)   # sp doesn't like NAs
SP <- SpatialPoints(map_df[coordinate_exists, c("Longitude", "Latitude")],
                    proj4string=CRS(crs_longlat)
)
SP.UTM <- spTransform(SP, CRS(crs_utm))
# Add transformed coords to data set
map_df$x[coordinate_exists] <- SP.UTM@coords[,1]
map_df$y[coordinate_exists] <- SP.UTM@coords[,2]

# Plot map 
ggplot(map_df, aes(x, y)) + 
  geom_path() +
  coord_fixed()

```


## 5. Distance from point along coast  

### Make 'coastsegment_distance'   
Distances along coast segments
```{r}

#
# Distances for start points of the coast segments
#
segment_dx <- diff(coast$x)/1000
segment_dy <- diff(coast$y)/1000
coastsegment_distance <- sqrt(segment_dx^2 + segment_dy^2) %>% cumsum()
coastsegment_distance <- c(0, coastsegment_distance)
coastsegment_distance

```

### Test 'get_distance_along_coast' and 'check_distance_along_coast'  
```{r}

# Usual case: the point is on the normal to at least one of the edges
check_distance_along_coast(point = list(x = 600000, y = 6550000), 
                           df_segments = coast, 
                           df_segments_distances = coastsegment_distance)

# Unusual case: the point is by a "concave" edge on the coast
check_distance_along_coast(point = list(x = 1285975, y = 7880861), 
                           df_segments = coast, 
                           df_segments_distances = coastsegment_distance)

 

if (FALSE){
  check_distance_along_coast(point = list(x = 500000, y = 6550000), 
                             df_segments = coast, 
                             df_segments_distances = coastsegment_distance)
  
  check_distance_along_coast(point = list(x = 500000, y = 6450000), 
                             df_segments = coast, 
                             df_segments_distances = coastsegment_distance)
  
}


```


## 6. Add Dist_along_coast to station data  

### Add UTM coordinates (x,y)  
```{r}

df_stations <- as.data.frame(df_stations)

coordinate_exists <- !is.na(df_stations$Lon)   # sp doesn't like NAs
SP <- SpatialPoints(df_stations[coordinate_exists, c("Lon", "Lat")],
                    proj4string=CRS(crs_longlat)
)
SP.UTM <- spTransform(SP, CRS(crs_utm))
# Add transformed coords to data set
df_stations$x[coordinate_exists] <- SP.UTM@coords[,1]
df_stations$y[coordinate_exists] <- SP.UTM@coords[,2]


```

### Plot  
```{r}

ggplot(map_df, aes(x, y)) + 
  geom_path() +
  coord_fixed() +
  geom_path(data = coast, color = "blue") +
  geom_point(data = df_stations, color = "red3") 

```


### Get Dist_along_coast  
```{r}

get_distance_along_coast_s <- safely(get_distance_along_coast)

rows <- 1:nrow(df_stations)

result_list <- rows %>%
  map(~ get_distance_along_coast_s(
    point = list(x = df_stations$x[.], y = df_stations$y[.]), 
    df_segments = coast, 
    df_segments_distances = coastsegment_distance)) %>%
  purrr::transpose()

# Sum up results
ok <- result_list$error %>% map_lgl(is.null)
dist <- result_list$result[ok] %>% map_dbl(~.$distance)

# Number that didnæt work
sum(!ok)

```

### Check out the ones with error, if necessary
```{r}

if (sum(!ok) > 0){

    i <- which(!ok)[1]
  
  # debugonce(get_distance_along_coast_all)
  check_distance_along_coast(
    point = list(x = df_stations$x[i], y = df_stations$y[i]), 
    df_segments = coast, 
    df_segments_distances = coastsegment_distance)
  
}

```

### Add Dist_along_coast  

```{r}

df_stations$Dist_along_coast <- NA
df_stations$Dist_along_coast[ok] <- dist

```

## 7. Save  
```{r}

saveRDS(df_stations, "Data/103_Selected_stations.rds")

```

