---
title: "104_Isotopes_and_trophic_level"
author: "DHJ"
date: "19 5 2020"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide 
---


Analysing trophic level relative to position along coast  


```
Mail fra Anders 13.05.2020:  
  
Trofisk nivå for de enkelte torskeindivider regnes ut slik:
  
`TL_torsk = 2 + (Delta15N_torsk - Delta15N_blåskjell)/3.8`     
  
Her er `Delta15N_torsk` verdien av d15N for den enkelte torsken, mens `Delta15N_blåskjell` er gjennomsnittlig verdi av d15N i blåskjell fra den nærmeste blåskjellstasjonen.  

Ligningen har som antakelse at alle blåskjell langs kysten er på trofisk nivå ca. 2 (altså at de er primærkonsumenter) og at d15N øker med 3.8 for hvert (hele) trofiske nivå i næringskjeden.  
```

## 1. Libraries  
```{r, warning=FALSE, message=FALSE, results='hide'}

library(forcats)   # fct_reorder()
library(ggplot2)
library(leaflet)
library(knitr)
library(purrr)

library(safejoin)  # package from https://github.com/moodymudskipper/safejoin 

library(sp)
library(kableExtra)

library(dplyr)            #   load last to avoid name conflicts such as MASS::select

crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"

source("103_Distance_along_coast_functions.R")

# environment(select)

```


## 2. Data

### Read files   
NOTE: the file `87_df_isotopes.rds` is created in the `Milkys` project and copied from there
```{r, results = 'hold'}

# Raw data  
dat <- readRDS("Data/101_Selected_data.rds") %>%
  mutate(STATION_CODE = case_when(
    STATION_CODE %in% "36A" ~ "36A1",
    TRUE ~ STATION_CODE)
    )

cat("\nRaw data: \n")
xtabs(~MYEAR, dat)

# Extra isotope data  
# created in the `Milkys` project and copied from there
dat_isotopes <- readRDS("Input_data/87_df_isotopes.rds") %>%
  mutate(STATION_CODE = case_when(
    STATION_CODE %in% "36A" ~ "36A1",
    TRUE ~ STATION_CODE)
    )

cat("\n\nIsotope data: \n")
xtabs(~MYEAR, dat_isotopes)
xtabs(~STATION_CODE, dat_isotopes)

# Station metadata
df_stations <- readRDS("Data/103_Selected_stations.rds")

# Station metadata needs to be summarised  
df_stations <- df_stations %>%
  filter(Station_Name != "Risøy, Østerfjord") %>%
  mutate(
    MSTAT = case_when(
      STATION_CODE %in% "I969" ~ "RH",
      TRUE ~ MSTAT)
  ) %>%
  group_by(STATION_CODE, Station_Name, MSTAT) %>%
  summarise_at(vars("Lat", "Lon", "Dist_along_coast"), mean, na.rm = TRUE) %>%
  mutate(
    Dist_along_coast = case_when(
      STATION_CODE %in% c("19N","19B") ~ 3000,    # Svalbard stations  
      TRUE ~  Dist_along_coast)
  )


check <- df_stations %>%
  group_by(STATION_CODE) %>%
  mutate(n = n()) %>%
  filter(n > 1)

if (nrow(check) > 0){
  stop("Some STATION_CODE occurs more than one time")
}

```


#### Stations by year    
```{r}

dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2014) %>%
  xtabs(~STATION_CODE + MYEAR, .) %>%
  knitr::kable()
  

```

### Add position       
Using `df_stations`   
Position lacking for stations 19B (Barents Sea - no blue mussel close anyway)  
```{r, results = 'hold'}

dat_isotopes <- dat_isotopes %>%
  safe_left_join(df_stations %>% select(STATION_CODE, Lat, Lon, Dist_along_coast, MSTAT), 
                 na_matches = "never",
                 check = "CV",
                 by = "STATION_CODE")

check <- dat_isotopes %>%
  group_by(STATION_CODE) %>%
  summarise(Lat = first(Lat), .groups = "drop")

cat("Positions added for", sum(!is.na(check$Lat)), "stations \n")
cat("Positions lacking for", sum(is.na(check$Lat)), "stations \n")
if (sum(is.na(check$Lat)) > 0)
  cat("- positions lacking for stations", check$STATION_CODE[is.na(check$Lat)] %>% paste(collapse = ", "), "\n")

```
### Data for plotting maps   
From script 122 (without adaption)      
  
Mapdata  
```{r}
#
# Get Norway map data
#
test <- maps::map("world", "Norway", plot = FALSE)   # map data for Norway - this is just to get region names
sel <- grepl("Svalbard", test$names) | test$names == "Norway:Jan Mayen"  # select Svalbard + Jan Mayen
# test$names[!sel]
map <- maps::map("world", test$names[!sel], exact = TRUE, plot = FALSE)  # Norway w/o Svalbard + Jan Mayen
mapdata <- data.frame(Longitude = map$x, Latitude = map$y)

#
# Add UTM coordinates (x and y) to map
#
coordinate_exists <- !is.na(mapdata$Longitude)   # sp doesn't like NAs
SP <- sp::SpatialPoints(mapdata[coordinate_exists, c("Longitude", "Latitude")],
                    proj4string=CRS(crs_longlat)
)
SP.UTM <- sp::spTransform(SP, CRS(crs_utm))
# Add transformed coords to data set
mapdata$x[coordinate_exists] <- SP.UTM@coords[,1]
mapdata$y[coordinate_exists] <- SP.UTM@coords[,2]




```

'Coast' - line going along coast  
* See plot at end of script   
```{r}
#
# "Coast" data (coordinates for segments along the coast)
#
coast <- readRDS("Data/102_coast_coordinates.rmd")

#
# Make 'coastsegment_distance'   
#
# Distances for start points of the coast segments
segment_dx <- diff(coast$x)/1000
segment_dy <- diff(coast$y)/1000
coastsegment_distance <- sqrt(segment_dx^2 + segment_dy^2) %>% cumsum()
coastsegment_distance <- c(0, coastsegment_distance)

```

'coast_points' - points/text to plot along 'coast'   
```{r}
# Get positions for these km's:
coast_points <- 
  c(0, 500, 1000, 1500, 2000, 2500, 2685) %>% map_df(~get_point_on_coastline(.))

# Direction of text labels:
coast_points$Text_direction <- "West"
coast_points$Text_direction[c(1,6,7)] <- "East"

SP.utm <- SpatialPoints(coast_points[,c("x", "y")], 
                        proj4string=CRS(crs_utm)
                        )
SP.longlat <- spTransform(SP.utm, CRS(crs_longlat))
coast_points$Longitude <- SP.longlat@coords[,1]
coast_points$Latitude <- SP.longlat@coords[,2]

```


```{r}
source("103_Distance_along_coast_functions.R")

```

```{r}
  
plot_coast_distance <- function(map, coast){
  
    # Get positions for km's to show:
  points <- c(0, 500, 1000, 1500, 2000, 2500, 2685) %>% map_df(~get_point_on_coastline(.))
  
  
  # Direction of text labels:
  points$Text_direction <- "West"
  points$Text_direction[c(1,6,7)] <- "East"
  
  # PLot
  gg2 <- ggplot(map, aes(x, y)) +
    geom_path() +
    coord_fixed() +
    geom_path(data = coast, color = "red") +
    geom_point(data = points, color = "blue") +
    geom_text(data = points %>% filter(Text_direction == "West"), 
              aes(x = x - 20000, label = paste(distance, "km")), 
              color = "blue", hjust = 1, size = rel(3)) +
    geom_text(data = points %>% filter(Text_direction == "East"), 
              aes(x = x + 20000, label = paste(distance, "km")), 
              color = "blue", hjust = 0, size = rel(3)) +
    expand_limits(x = c(min(mapdata$x, na.rm = TRUE) - 150000,
                        max(mapdata$x, na.rm = TRUE) + 200000)) +
    theme_minimal() +
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      panel.grid = element_blank()
    )
  
gg2
}


# debugonce(plot_coast_distance)
plot_coast_distance(mapdata, coast)


```

## 3. Calculate means of Delta15N     
```{r}

dat_isotopes_means1 <- dat_isotopes %>%
  group_by(TISSUE_NAME, STATION_CODE, Lat, Lon, Dist_along_coast, MYEAR) %>%
  summarise_at(c("Delta13C", "Delta15N"), mean, na.rm = TRUE) %>%
  ungroup() %>%
  mutate(STATION_CODE = fct_reorder(STATION_CODE, Dist_along_coast),
         Organism = case_when(
           grepl("B", STATION_CODE) ~ "Cod",
           grepl("F", STATION_CODE) ~ "Flatfish",
           TRUE ~ "Blue mussel"
         ))

```


## 4. Plot Delta15N means, tile plots {.tabset}   

### Cod (muscle)  
```{r, fig.height=4, fig.width=9}

dat_isotopes_means1 %>%
  filter(TISSUE_NAME %in% "Muskel") %>%
  ggplot(aes(STATION_CODE, MYEAR, fill = Delta15N)) +
  geom_tile() +
  viridis::scale_fill_viridis() +
  scale_y_reverse() +
  labs(title = "Muskel")

```

### Blue mussel 
```{r, fig.height=4, fig.width=9}

dat_isotopes_means1 %>%
  filter(TISSUE_NAME %in% "Whole soft body") %>%
  ggplot(aes(STATION_CODE, MYEAR, fill = Delta15N)) +
  geom_tile() +
  viridis::scale_fill_viridis() +
  scale_y_reverse() +
  theme(axis.text.x = element_text(angle = -45, hjust = 0)) +
  labs(title = "Blue mussel")


```
## 5. Plot Delta15N means by distance along coast, tile plots {.tabset}   

### Cod (muscle)  
```{r, fig.height=5, fig.width=7}

dat_isotopes_means1 %>%
  filter(TISSUE_NAME %in% "Muskel") %>%
  ggplot(aes(Dist_along_coast, Delta15N)) +
  geom_point(aes(fill = MYEAR), shape = 21, size = rel(2)) +
  viridis::scale_fill_viridis() +
  geom_smooth(method = 'loess', formula = 'y ~ x') +
  labs(title = "Fish")

```


### Blue mussel  
```{r, fig.height=5, fig.width=7}

dat_isotopes_means1 %>%
  filter(TISSUE_NAME %in% "Whole soft body") %>%
  ggplot(aes(Dist_along_coast, Delta15N)) +
  geom_point(aes(fill = MYEAR), shape = 21, size = rel(2)) +
  viridis::scale_fill_viridis() +
  geom_smooth(method = 'loess', formula = 'y ~ x') +
  labs(title = "Blue mussel")

```



## 6. Find closest mussel station for each cod station   

### Leaflet map   

```{r}

dat_isotopes_stations <- dat_isotopes_means1 %>%
  group_by(TISSUE_NAME, STATION_CODE, Lat, Lon) %>%
  summarise(Years = paste(MYEAR, collapse = ", "), .groups = "drop") 


df <- dat_isotopes_stations %>% 
  filter(TISSUE_NAME %in% c("Muskel", "Whole soft body") & !is.na(Lat))

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = case_when(
    df$TISSUE_NAME == "Whole soft body" ~ "blue",
    df$TISSUE_NAME == "Muskel" ~ "red")
)

leaflet(df) %>%
  addTiles() %>%
  addAwesomeMarkers(~Lon, ~Lat, icon = icons,
                    label =  ~STATION_CODE)
  
```


### Closest/corresponding mussel station   
Set based on map above  
```{r}

#
# 19B = Svalbard - no bue mussel stations close  
#

data_closest_mussel_station <- read.csv(textConnection("
Cod_station, Mussel_station
30B,I304
33F,35A
02B,I024
36F,36A1
71B,I712
13B,I133
15B,15A
23B,22A
24B,I241
28B,28A2
36B,36A1
53B,56A
80B,91A2
96B,I969
98B1,98A2
43B2,98A2
45B2,98A2
10B,11X
"),
stringsAsFactors = FALSE
)

# Pretty far from eacah other: 80B, 91A2

```

### Table of corresponding cod/mussel stations  
```{r}

table_coupling_stations <- df_stations %>%
  filter(grepl("B", STATION_CODE)) %>%
  select(STATION_CODE, Station_Name, Dist_along_coast) %>%
  mutate(Dist_along_coast = round(Dist_along_coast)) %>%
  rename(Cod_station = STATION_CODE,
         Cod_station_name = Station_Name,
         `Dist along coast (km)` = Dist_along_coast) %>%
  inner_join(
    data_closest_mussel_station, 
    by = "Cod_station") %>%
  left_join(df_stations %>% 
              select(STATION_CODE, Station_Name) %>%
              rename(Mussel_station = STATION_CODE,
                     Mussel_station_name = Station_Name),
            by = "Mussel_station") %>%
  arrange(`Dist along coast (km)`)

# Remove underscores in names
names(table_coupling_stations) <- gsub("_", " ", names(table_coupling_stations), fixed = TRUE)

table_coupling_stations %>%
  kbl(escape = FALSE) %>%
  kable_classic()

```




### Plot N15 for these cod and mussel stations  {.tabset}  

#### Cod
```{r}

dat_isotopes %>%
  filter(TISSUE_NAME %in% "Muskel" & 
           grepl("B", STATION_CODE) & 
           STATION_CODE %in% data_closest_mussel_station$Cod_station) %>%
  ggplot(aes(MYEAR, Delta15N)) +
  geom_jitter(width = 0.1) +
  facet_wrap(vars(STATION_CODE))

```

#### Blue mussel
```{r}
dat_isotopes %>%
  filter(TISSUE_NAME %in% "Whole soft body" &
         STATION_CODE %in% data_closest_mussel_station$Mussel_station) %>%
  ggplot(aes(MYEAR, Delta15N)) +
  geom_jitter(width = 0.1) +
  facet_wrap(vars(STATION_CODE))

```

### Summarise mussel data  
For each station (not year-specific means)  
```{r}

data_mussel_means <- dat_isotopes %>%
  filter(TISSUE_NAME %in% "Whole soft body" & 
           STATION_CODE %in% data_closest_mussel_station$Mussel_station) %>%
  filter(!(STATION_CODE %in% "I024" & MYEAR %in% 2017)) %>%
  group_by(STATION_CODE) %>%
  summarise_at(c("Delta13C", "Delta15N"), mean, na.rm = TRUE) %>%
  rename(Delta13C_mussel = Delta13C,
         Delta15N_mussel = Delta15N) %>%
  ungroup()

data_closest_mussel_station <- data_closest_mussel_station %>%
  left_join(data_mussel_means, by = c("Mussel_station" = "STATION_CODE"))

```



## 7. Add mussel data columns to main data   
### a. Add mussel and calculate trophic level (TL)   
All data, i.e. one line per parameter and sample, for all parameters  
* Note: suitable for correlating contaminants with TL  
* Not the data to use for looking at TL itself, use dat3 for that    
```{r}

dat2 <- dat %>%
  # Add Delta13C, Delta15N for each individual
  left_join(
    dat_isotopes %>% 
      select(MYEAR, STATION_CODE, TISSUE_NAME, SAMPLE_NO2, Delta13C, Delta15N), 
    by = c("MYEAR", "STATION_CODE", "TISSUE_NAME", "SAMPLE_NO2")
  ) %>% # View()
  # Add Delta13C, Delta15N for closest mussel station
  left_join(
    data_closest_mussel_station, 
    by = c("STATION_CODE" = "Cod_station")) %>%
  ungroup() %>% 
  # Calculate trophic level (TL)
  mutate(
    TL = case_when(
      TISSUE_NAME %in% c("Lever", "Muskel") ~ 2 + (Delta15N - Delta15N_mussel)/3.8,
      TISSUE_NAME %in% "Whole soft body" ~ 2)
    )  %>%
  # Add Lat, Lon, Dist_along_coast, MSTAT
  safe_left_join(df_stations %>% select(STATION_CODE, Lat, Lon, Dist_along_coast, MSTAT), 
                 na_matches = "never",
                 check = "CV",
                 by = "STATION_CODE") %>%
  # Make STATION_CODE factor levels to follow 'Dist_along_coast'
  mutate(STATION_CODE = fct_reorder(STATION_CODE, Dist_along_coast))

cat("dat2:", nrow(dat2), "lines \n")

# dat2$STATION_CODE %>% levels()

```


### b. Keep only isotopes and TL data    
Plus LNMEA and FAT_PERC
```{r}
dat3 <- dat2 %>%
  filter(TISSUE_NAME %in% "Muskel" & !is.na(TL)) %>%
  group_by(TISSUE_NAME, MYEAR, STATION_CODE, Lat, Lon, Dist_along_coast, MSTAT, SAMPLE_NO2) %>%
  summarise(across(c(Delta15N, Delta15N_mussel, TL, LNMEA, FAT_PERC), first),
            .groups = "drop") %>%
  mutate(MYEAR_f = factor(MYEAR),
         STATION_CODE = fct_drop(STATION_CODE)
         ) 

cat("dat3:", nrow(dat3), "lines \n")

```

### c. Save   
```{r}

#
# These data are used in script 105
#

saveRDS(dat2, "Data/104_dat2.rds")
saveRDS(dat3, "Data/104_dat3.rds")
saveRDS(data_closest_mussel_station, "Data/104_data_closest_mussel_station.rds")

```

## 8. Remove excessively low/high trophic level  

### Remove 5 outliers   
See "code" for cut-off values  
```{r}

dat3 <- dat3 %>%
  mutate(
    Outlier = case_when(
      TL > 5.6 ~ TRUE,
      TL < 2.8 ~ TRUE,
      TRUE ~ FALSE)
    )

xtabs(~Outlier, dat3)

ggplot(dat3, aes(LNMEA, TL, color = Outlier)) + 
  geom_point() +
  scale_color_manual(values = c("grey70", "black")) +
  facet_wrap(vars(STATION_CODE)) +
  labs(title = "Cod trophic level") +
  theme_bw()

dat3 <- dat3 %>% 
  filter(!Outlier) %>%
  select(-Outlier)

```

## 9. Plots {.tabset}  
Repating the Delta15N plot shown above  

### Cod Delta15N    
```{r, fig.height=4, fig.width=9}

dat_isotopes_means1 %>%
  filter(TISSUE_NAME %in% "Muskel" & grepl("B", STATION_CODE)) %>%
  ggplot(aes(STATION_CODE, MYEAR, fill = Delta15N)) +
  geom_tile() +
  viridis::scale_fill_viridis() +
  scale_y_reverse() +
  labs(title = "Muskel")

```

### Median cod TL    
```{r, fig.height=4, fig.width=9}

dat3 %>%
  group_by(MYEAR, STATION_CODE) %>%
  summarise(TL = median(TL), .groups = "drop") %>%
  ggplot(aes(STATION_CODE, MYEAR, fill = TL)) +
  geom_tile() +
  viridis::scale_fill_viridis() +
  scale_y_reverse() +
  labs(title = "Cod trophic level") 


```

### TL boxplots  
```{r, fig.height=6, fig.width=9}

ggplot(dat3, aes(factor(MYEAR), TL)) + 
  geom_boxplot() +
  facet_wrap(vars(STATION_CODE)) +
  labs(title = "Cod trophic level") 

```

  
### TL vs length    
```{r, fig.height=6, fig.width=9}

ggplot(dat3, aes(LNMEA, TL)) + 
  geom_point(aes(fill = MYEAR_f), pch = 21, size = rel(2)) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  geom_smooth(method = "lm", formula = 'y ~ x') +
  facet_wrap(vars(STATION_CODE)) +
  labs(y = "Trophic level", x = "Cod length (mm)") 

```
  
### TL vs Delta15N    
```{r, fig.height=6, fig.width=9}

ggplot(dat3, aes(Delta15N, TL)) + 
  geom_point(aes(fill = STATION_CODE), pch = 21, size = rel(2)) +
  viridis::scale_fill_viridis(discrete = TRUE)

```

## 10. Mixed-model analyses  
### Load mixed-model analyses   
* Models were estimated using script 105, we just load the saved results here (to save time)       
* Models estimated using both REML (gives the best estimates) and ML (can be used for hypothesis testing using ANOVA)   
    + REML = restricted maximum likelihood  
    + ML = maximum likelihood    
```{r}

#
# Models 
#

model_list <- readRDS("Data/105_model_list.rds")

# The formula for each REML model  
model_list[1:3] %>% map(formula)

# name of models in script 105:
# list(fm2b, fm3a, fm3b, fm2b_null_ml, fm2b_ml, fm3a_ml, fm3b_ml)
# Model 1-3 are estimated using REML 
# Model 4: null model estimated using ML 
# Model 5-7 = model 1-3 estimated using ML 

mod_station <- model_list[[1]]       
mod_station_length <- model_list[[2]]
mod_station_length_x <- model_list[[3]]
mod_ml_null <- model_list[[4]]
mod_ml_station <- model_list[[5]]       
mod_ml_station_length <- model_list[[6]]
mod_ml_station_length_x <- model_list[[7]]


#
# Predictions  
# Made using model_list 1-3 above (i.e. the REML models)  
#

# name of predic in script 105:
# list(newdat, pred_3a, pred_3b)
model_predictions <- readRDS("Data/105_model_predictions.rds")

# Set names so they 
pred_station <- model_predictions[[1]]
pred_station_length <- model_predictions[[2]]
pred_station_length_x <- model_predictions[[3]]


```

### ANOVA of models  
* Using the ML (max. likelihood models)  
* Clearly indicates that station, length and the station*length interaction all are significant  
* I.e., there are significant differences in the length_TL relationship among stations  
```{r}

anova(mod_ml_null, mod_ml_station, mod_ml_station_length, mod_ml_station_length_x)

```

### Distance data - to add to predicted data  
```{r}
df_stations_plot <- df_stations %>%
  filter(STATION_CODE %in% pred_station$STATION_CODE) %>%
  select(STATION_CODE, Station_Name, Lon, Lat, Dist_along_coast) %>%
  mutate(
    Station_y = case_when(
      STATION_CODE %in% c("30B","53B") ~ 0,
      TRUE ~ -0.04)
  ) %>%
  mutate(
    Place = case_when(
      STATION_CODE %in% "30B" ~ "Oslo",
      STATION_CODE %in% "13B" ~ "Kristiansand",
      STATION_CODE %in% "24B" ~ "Bergen",
      STATION_CODE %in% "80B" ~ "Trondheim",
      STATION_CODE %in% "43B2" ~ "Tromsø",
      STATION_CODE %in% "10B" ~ "Kirkenes")
  )

```

### Plot function  
```{r}  

# df_stations_plot is given globally  
plot_pred_distance <- function(model_predictions, ylabel, length = NULL, 
                               station_data = df_stations_plot){
  if (is.null(length)){
    df <- model_predictions
  } else {
    df <- model_predictions %>%
      filter(LNMEA == length)
  }
  df <- df %>%
    safe_left_join(station_data,
                   by = "STATION_CODE", na_matches = "never",
                   check = "CV")
  ggplot(df, aes(Dist_along_coast, TL)) +
    geom_pointrange(aes(ymin = plo, ymax = phi)) +
    geom_text(aes(y = min(plo) + Station_y, label = STATION_CODE), 
              angle = 40, size = rel(3), color = "blue3") +
    geom_text(aes(y = max(phi) + 0.02, label = Place), 
              angle = 0, size = rel(3), color = "blue3") +
    labs(x = "Station code", y = ylabel) +
    theme_bw()
}

```


## 11. Plots of station estimates {.tabset}   
* All models use "year" as a random factor, station effect is estimated on the year level   
* CIs estimated using Ben Bolker's method, and are based on fixed-effects uncertainty only, i.e. the confidence interval for the station effect  

### Model: station only
```{r}

gg <- plot_pred_distance(pred_station, "Estimated trophic level")
gg

```

### Model: station + length (40 cm)  
Model including station and length (additive effect). Predictions for 50 cm cod. For other lengths, only the the y axis would change, not the relative heights of each station  
```{r}

length <- 400
ylabel <- paste0("Estimated trophic level (", length/10, "cm cod)")
gg <- plot_pred_distance(pred_station_length, ylabel, length = length)
gg

```


### Model: station x length  (40 cm)   
Model including station, length and the station x length interaction. Predictions for 40 cm cod. 
```{r}

length <- 400
ylabel <- paste0("Estimated trophic level (", length/10, "cm cod)")
gg <- plot_pred_distance(pred_station_length_x, ylabel, length = length)
gg

```


### Model: station x length  (70 cm)   
Model including station, length and the station x length interaction. Predictions for 40 cm cod. 
```{r}

length <- 700
ylabel <- paste0("Estimated trophic level (", length/10, "cm cod)")
gg <- plot_pred_distance(pred_station_length_x, ylabel, length = length)
gg

```


## 12. Mixed model analysis of distance along coast {.tabset}   
  
### a. Distance along coast  
NOTE: Scale is 1000 kms, which is why estimate and CI is 1000x higher than in c 
```{r}

# Read results from script 105  
model_list_brm <- readRDS("Data/105_model_list_brm.rds")

model_list_brm[[1]]

fixed <- summary(model_list_brm[[1]])$fixed
fixed <- as.data.frame(fixed)

fixed %>%
  kable()

```
  
### Distance along coast, length-corrected        
```{r}

model_list_brm[[3]]

fixed <- summary(model_list_brm[[3]])$fixed
fixed <- as.data.frame(fixed)

fixed %>%
  kable()

```

### Distance along coast, length-corrected, plot  
LNMEA = fish length, Dista_along_coast = distance along coast   
```{r}

fixed$Effect <- rownames(fixed)

ggplot(fixed %>% filter(Effect != "Intercept"), 
       aes(Effect, Estimate)) +
  geom_pointrange(aes(ymin = `l-95% CI`, ymax = `u-95% CI`)) +
  geom_hline(yintercept = 0)


```



## 13. Maps and station table {.tabset}  

### Map  
```{r, fig.width=6, fig.height=7}

stations_right <- c("02B", "30B", "13B", "53B", "10B")

gg_map <- ggplot(mapdata, aes(Longitude, Latitude)) + 
  geom_path(color = "grey50") +
  coord_map("lambert", parameters = c(10.4, 59.3), 
            xlim = c(5, 28), ylim = c(57.9, 72)) +
  geom_point(data = df_stations_plot, aes(Lon, Lat), color = "red3") +
  geom_text(data = df_stations_plot %>% filter(STATION_CODE %in% stations_right), 
            aes(Lon, Lat, label = STATION_CODE),
            hjust = -0.2, color = "red3") +
  geom_text(data = df_stations_plot %>% filter(!STATION_CODE %in% stations_right), 
            aes(Lon, Lat, label = STATION_CODE),
            hjust = 1.2, color = "red3") +
  theme_minimal() +
  theme(axis.title = element_blank())

gg_map

```


### Map with coastal distance    
```{r, fig.width=6, fig.height=7}

stations_right <- c("02B", "30B", "13B", "53B", "10B")

gg_map +
  geom_path(data = coast, color = "blue") +
  geom_point(data = coast_points, color = "blue") +
  geom_text(data = coast_points %>% filter(Text_direction == "West"), 
            aes(label = paste(distance, "km")), color = "blue", hjust = 1.2) +
  geom_text(data = coast_points %>% filter(Text_direction == "East"), 
            aes(label = paste(distance, "km")), color = "blue", hjust = -0.2) +
  coord_map("lambert", parameters = c(10.4, 59.3), 
            xlim = c(2, 30), ylim = c(57.9, 72))
  
  
```

### Station table  
```{r}

df_stations_plot %>%
  select(STATION_CODE:Dist_along_coast) %>%
  arrange(Dist_along_coast) %>%
  mutate(across(c(Lon,Lat), round, digits = 4)) %>%
  mutate(Dist_along_coast = round(Dist_along_coast, digits = 0)) %>%
  rename(`Station code` = STATION_CODE,
         `Station name` = Station_Name,
         `Distance along coast`= Dist_along_coast) %>%
  kable()

```



