---
title: "105_Trophic_level_mixed_models"
author: "DHJ"
date: "23 9 2020"
output: 
  html_document:
    keep_md: true  
    toc: true
    toc_float: true
    
---

## 1. Libraries  
```{r, message=FALSE, warning=FALSE, results='hide'}

library(ggplot2)
library(lme4)
library(arm)
library(merTools)    # predictInterval()
library(dplyr)       # load dplyr last, otherwise select() will use select() from package MASS 

library(brms)


```

## 2. Data  
```{r, results='hold'}

dat2 <- readRDS("Data/104_dat2.rds")
cat("Data/104_dat2.rds: ", nrow(dat2), "lines \n")

dat3_uncleaned <- readRDS("Data/104_dat3.rds")
cat("Data/104_dat3.rds: ", nrow(dat3_uncleaned), "lines \n\n")

data_closest_mussel_station <- readRDS("Data/104_data_closest_mussel_station.rds")

xtabs(~STATION_CODE +  MYEAR, dat3_uncleaned)

```

## 3. Plots of raw data   

### Raw data  
```{r}

ggplot(dat3_uncleaned, aes(factor(MYEAR), TL)) + 
  geom_boxplot() +
  facet_wrap(vars(STATION_CODE)) +
  labs(title = "Cod trophic level") 

```
### TL vs length    
```{r}

ggplot(dat3_uncleaned, aes(LNMEA, TL, color = factor(MYEAR))) + 
  geom_point() +
  facet_wrap(vars(STATION_CODE)) +
  labs(title = "Cod trophic level") 

```


## 4. Make dat3  

### Pick outliers  
```{r}

dat3_uncleaned <- dat3_uncleaned %>%
  mutate(
    Outlier = case_when(
      TL > 5.6 ~ TRUE,
      TL < 2.8 ~ TRUE,
      TRUE ~ FALSE)
    )

xtabs(~Outlier, dat3_uncleaned)

ggplot(dat3_uncleaned, aes(LNMEA, TL, color = Outlier)) + 
  geom_point() +
  scale_color_manual(values = c("grey70", "black")) +
  facet_wrap(vars(STATION_CODE)) +
  labs(title = "Cod trophic level - identifying outliers") +
  theme_bw()

```


### Remove outliers  
```{r}

dat3 <- dat3_uncleaned %>% filter(!Outlier)

```


### Means  
```{r}

dat3 %>%
  group_by(MYEAR, STATION_CODE) %>%
  summarise(TL = median(TL), .groups = "drop") %>%
  ggplot(aes(STATION_CODE, MYEAR, fill = TL)) +
  geom_tile() +
  viridis::scale_fill_viridis() +
  scale_y_reverse() +
  labs(title = "Cod trophic level") 

```

## 5. STATION_CODE as random factor (i.e., 2 random effects)  
```{r, cache=TRUE}

fm2 <- lmer(
  formula = TL ~ 1 + (1|MYEAR_f) + (1|STATION_CODE), 
  data = dat3
)
summary(fm2)

```

### Check random effects  
This doesn't look right  
```{r, results='hold'}

eff <- ranef(fm2 , drop = TRUE)

eff$STATION_CODE
attr(eff$STATION_CODE, "postVar")  

df <- tibble(
  STATION_CODE = names(eff$STATION_CODE) %>% factor(levels = levels(dat3$STATION_CODE)),
  Estimate = eff$STATION_CODE,
  SD = attr(eff$STATION_CODE, "postVar")  
)

ggplot(df, aes(STATION_CODE, Estimate)) +
  geom_pointrange(aes(ymin = Estimate - 2*SD, ymax = Estimate + 2*SD))

```

## 6.  STATION_CODE as fixed factor (fm2b)   
* 'STATION_CODE' is to be evaluated within years   
    + See http://www.rensenieuwenhuis.nl/r-sessions-16-multilevel-model-specification-lme4/
```{r, cache=TRUE}
fm2b <- lmer(
  formula = TL ~ STATION_CODE + (1|MYEAR_f), 
  data = dat3
)
summary(fm2b)

# Get ML model (max. likelihood estimates) for anova
fm2b_ml  <- update(fm2b , REML = FALSE)

```
### Hypothesis testing using ANOVA    
https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#methods-for-testing-single-parameters  
```{r, cache=TRUE}

# Null model
fm2b_null_ml <- lmer(
  formula = TL ~ 1 + (1|MYEAR_f), 
  data = dat3,
  REML = FALSE
)

anova(fm2b_null_ml, fm2b_ml)


```


### Estimates from station coefficients  
"Simple-minded" solution  
- Plot shown in next chunk
- Note that 02B disappears, it is the Intercept   
```{r}


df <- summary(fm2b)$coe
df <- df %>%
  as.data.frame() %>%
  rename(SD = `Std. Error`) %>%
  mutate(
    STATION_CODE = sub("STATION_CODE", "", rownames(df))  %>% factor(levels = levels(dat3$STATION_CODE))
         )


gg2b_1 <- ggplot(df[-1,], aes(STATION_CODE, Estimate)) +
  geom_pointrange(aes(ymin = Estimate - 2*SD, ymax = Estimate + 2*SD))  +
  labs(title = "CI from fixed-effect coefficients (lacking 02B)") 

# gg_2b_1

```

### Estimates using Ben Bolker's code  
https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#lme4  
```{r}

model <- fm2b

newdat <- data.frame(
  STATION_CODE = factor(levels(dat3$STATION_CODE), levels = levels(dat3$STATION_CODE))
  )
newdat$TL <- predict(model, newdat, re.form = NA)

mm <- model.matrix(terms(model),newdat)
## or newdat$distance <- mm %*% fixef(model)

pvar1 <- diag(mm %*% tcrossprod(vcov(model), mm))
tvar1 <- pvar1 + VarCorr(model)$MYEAR_f[1]  ## random effect here. must be adapted for more complex models
cmult <- 2 ## could use 1.96
newdat <- data.frame(
    newdat
    , plo = newdat$TL - cmult*sqrt(pvar1)
    , phi = newdat$TL + cmult*sqrt(pvar1)
    , tlo = newdat$TL - cmult*sqrt(tvar1)
    , thi = newdat$TL + cmult*sqrt(tvar1)
)


gg2b_2 <- ggplot(newdat, aes(STATION_CODE, TL)) +
  geom_pointrange(aes(ymin = plo, ymax = phi)) +
  labs(title = "CI based on fixed-effects uncertainty (confidence interval)")

gg2b_3 <- ggplot(newdat, aes(STATION_CODE, TL)) +
  geom_pointrange(aes(ymin = tlo, ymax = thi)) +
  labs(title = "CI based on fixed uncertainty + random effect variance (prediction interval)")

gg2b_1
gg2b_2
gg2b_3

```
### Estimates using merTools::predictInterval    
See https://stats.stackexchange.com/a/167059/13380   
This looks like the prediction interval?  
```{r}

newdat2 <- expand.grid(
    STATION_CODE = factor(levels(dat3$STATION_CODE), levels = levels(dat3$STATION_CODE)),
    MYEAR_f = levels(dat3$MYEAR_f)
    )

preds <- predictInterval(fm2b, newdata = newdat2, which = "fixed", n.sims = 999)
# str(preds)
newdat2 <- bind_cols(newdat2, preds)

# ggplot(newdat2, aes(STATION_CODE, fit, color = MYEAR_f)) +
#   geom_point()

ggplot(newdat2, aes(STATION_CODE, fit, color = MYEAR_f)) +
  geom_pointrange(aes(ymin = lwr, ymax = upr), position = position_dodge(width = 0.55))


```




## 7. STATION_CODE + length (LNMEA) as fixed effects (fm3)   


### Add rescaled variables  
```{r}
dat3 <- dat3 %>%
  mutate(LNMEA_rescale = (LNMEA-500)/100,
         Dist_along_coast_rescale = (Dist_along_coast-1000)/1000)

```

### Estimate models  
* fm3a: additive station and length effects   
   - TL increase with length same on all stations   
* fm3b: additive station and length effects   
   - TL increase with length differs between stations   
* Code based on  
http://www.rensenieuwenhuis.nl/r-sessions-16-multilevel-model-specification-lme4/ 
```{r, cache=TRUE}

fm3a <- lmer(
  formula = TL ~ LNMEA + STATION_CODE + (1|MYEAR_f), 
  data = dat3
)

fm3b <- lmer(
  formula = TL ~ LNMEA*STATION_CODE + (1|MYEAR_f),  
  data = dat3
)


if (FALSE){
  # OLD VERSIONS
  fm3a <- lmer(
    formula = TL ~ LNMEA*STATION_CODE + (1 + STATION_CODE|MYEAR_f), 
    data = dat3
  )
  
  fm3b <- lmer(
    formula = TL ~ LNMEA*STATION_CODE + (1 + STATION_CODE|MYEAR_f), 
    data = dat3
  )
  
}

summary(fm3a)
summary(fm3b)

fm3a_ml <- update(fm3a, REML = FALSE)
fm3b_ml <- update(fm3b, REML = FALSE)

```

### ANOVA  
```{r}

anova(fm2b_ml, fm3a_ml, fm3b_ml)

```




### Estimates using Ben Bolker's code  
https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#lme4    

### Function for getting estimates from models 
```{r}

get_estimates_model3 <- function(model){

  newdat3 <- expand.grid(
    STATION_CODE = factor(levels(dat3$STATION_CODE), levels = levels(dat3$STATION_CODE)),
    LNMEA = seq(300, 800, 100)
  )
  
  newdat3$TL <- predict(model, newdat3, re.form = NA)
  
  mm <- model.matrix(terms(model),newdat3)
  ## or newdat3$distance <- mm %*% fixef(model)
  
  pvar1 <- diag(mm %*% tcrossprod(vcov(model), mm))
  tvar1 <- pvar1 + VarCorr(model)$MYEAR_f[1]  ## random effect here. must be adapted for more complex models
  cmult <- 2 ## could use 1.96
  newdat3 <- data.frame(
    newdat3
    , plo = newdat3$TL - cmult*sqrt(pvar1)
    , phi = newdat3$TL + cmult*sqrt(pvar1)
    , tlo = newdat3$TL - cmult*sqrt(tvar1)
    , thi = newdat3$TL + cmult*sqrt(tvar1)
  )
  
  newdat3
  
}

# 4debugonce(get_estimates_model3)

```


### Model 3a. additive station and length effects  
I.e., length effect is the same in all stations
```{r}

pred_3a <- get_estimates_model3(fm3a)

# Mainly for showing that lines are parallell  
gg3a_lines <- ggplot(pred_3a, aes(LNMEA, TL)) +
  geom_line() +
  facet_wrap(vars(STATION_CODE))

# 
gg3a_40 <- pred_3a %>%
  filter(LNMEA == 400) %>%
  ggplot(aes(STATION_CODE, TL)) +
  geom_pointrange(aes(ymin = plo, ymax = phi)) +
  labs(title = "TL for 40 cm cod (no station*length interaction)")

# Just for testing: this should be identical to the previous, 
# except the y szcael being a bit different  
gg3a_80 <- pred_3a %>%
  filter(LNMEA == 800) %>%
  ggplot(aes(STATION_CODE, TL)) +
  geom_pointrange(aes(ymin = plo, ymax = phi)) +
  labs(title = "TL for 80 cm cod (no station*length interaction)")

if (FALSE){
  gg3a_lines
  gg3a_40
  gg3a_70
}



```


### Model 3b. Interaction between station and length effects   
I.e., length effect differs among stations
```{r}

pred_3b <- get_estimates_model3(fm3b)

# Mainly for showing that lines are NOT parallell  
gg3b_lines <- ggplot(pred_3b, aes(LNMEA, TL)) +
  geom_ribbon(aes(ymin = plo, ymax = phi), fill = "lightblue") +
  geom_line() +
  geom_rug(data = dat3) +
  facet_wrap(vars(STATION_CODE))

# 
gg3b_40 <- pred_3b %>%
  filter(LNMEA == 400) %>%
  ggplot(aes(STATION_CODE, TL)) +
  geom_pointrange(aes(ymin = plo, ymax = phi)) +
  labs(title = "TL for 40 cm cod (with station*length interaction)")

# Just for testing: this should be identical to the previous, 
# except the y szcael being a bit different  
gg3b_70 <- pred_3b %>%
  filter(LNMEA == 700) %>%
  ggplot(aes(STATION_CODE, TL)) +
  geom_pointrange(aes(ymin = plo, ymax = phi)) +
  labs(title = "TL for 70 cm cod (with station*length interaction)")

gg3a_40
gg3b_40
gg3b_70
gg3b_lines



```

#### Using package brms   

Rough normalisation of LNMEA and Dist_along_coast
```{r}

dat3 <- dat3 %>%
  mutate(LNMEA_s = (LNMEA-500)/100,
         Dist_along_coast_s = (Dist_along_coast-1000)/1000)
  
```

Only distance effect  
```{r}

brm_3a <- brm(TL ~ Dist_along_coast_s + (1|STATION_CODE),
              data = dat3, 
              warmup = 1000, iter = 6000, 
              cores = 2, chains = 2, 
              seed = 123,
              control = list(max_treedepth = 12))  # 
summary(brm_3a)
summary(brm_3a)$fixed

```

Length effect only
```{r}


brm_3b <- brm(TL ~ LNMEA + (1 + LNMEA|STATION_CODE),  
              data = dat3, 
              warmup = 1000, iter = 3000, 
              cores = 2, chains = 2, 
              seed = 123)
summary(brm_3b)

summary(brm_3b) %>% str(1)
summary(brm_3b)$fixed

```

Distance + length  
Note: this took ca. 35 minutes  
```{r}

# Note: max_treedepth = 10 (default) resulter in error  
# Should not be increased by much - try 12, have never needed more than 15
# Ref: 
#   https://stats.stackexchange.com/a/296959/13380 


brm_3c <- brm(TL ~ LNMEA + Dist_along_coast + (1 + LNMEA|STATION_CODE),
              data = dat3, 
              warmup = 1000, iter = 6000, 
              cores = 2, chains = 2, 
              seed = 123,
              control = list(max_treedepth = 12))  # 
summary(brm_3c)
summary(brm_3c)$fixed



```


## 9. Distance along coast (on STATION_CODE level) (fm4)     
http://www.rensenieuwenhuis.nl/r-sessions-16-multilevel-model-specification-lme4/    

### Make station_yr and fairly normalized variables  
* station_yr: combination variable  
* `LNMEA_n` and `Dist_along_coast_n`   
```{r}

dat3 <- dat3 %>%
  mutate(station_yr = factor(STATION_CODE:MYEAR_f),
         LNMEA_n = (LNMEA/100) - 5,
         Dist_along_coast_n = (Dist_along_coast/1000) - 1)    # 

```

### Test plots  
```{r}

if (FALSE){
  
ggplot(dat3, aes(Dist_along_coast, TL)) + 
  geom_point() +
  facet_wrap(vars(MYEAR))

ggplot(dat3, aes(LNMEA_n, TL)) + 
  geom_point() +
  facet_wrap(vars(station_yr))

}

```



### lmer models  
Seemingly ok fits  
```{r}

fm4a <- lmer(
  formula = TL ~ LNMEA_n + 
    (1|station_yr), 
  data = dat3,
  REML = FALSE
)

fm4b <- lmer(
  formula = TL ~ LNMEA_n + 
    (LNMEA_n|station_yr), 
  data = dat3,
  REML = FALSE
)

fm4c <- lmer(
  formula = TL ~ LNMEA_n + Dist_along_coast_n +
    (LNMEA_n|station_yr), 
  data = dat3,
  REML = FALSE
)

summary(fm4a)
summary(fm4b)
summary(fm4c)

anova(fm4a, fm4b, fm4c)

```


### Try station_yr(station * year combination)  
Results in boundary (singular) fit
```{r}

dat3 <- dat3 %>%
  mutate(station_yr = factor(STATION_CODE:MYEAR_f))
# xtabs(~station_yr, dat3)

fm4a <- lmer(
  formula = TL ~ LNMEA + 
    (1|station_yr), 
  data = dat3
)
summary(fm4a)

fm4b <- lmer(
  formula = TL ~ LNMEA + 
    (LNMEA|station_yr), 
  data = dat3,
  REML = FALSE
)
summary(fm4b)


fm4a <- lmer(
  formula = TL ~ Dist_along_coast + 
    (Dist_along_coast|STATION_CODE/MYEAR), 
  data = dat3
)

fm4a <- lmer(
  formula = TL ~ Dist_along_coast + 
    (1 + Dist_along_coast|STATION_CODE/MYEAR), 
  data = dat3
)

fm4a <- lmer(
  formula = TL ~ (1 + Dist_along_coast|STATION_CODE/MYEAR), 
  data = dat3
)

```


## 8. Save  
```{r}

model_list <- list(fm2b, fm3a, fm3b, fm2b_null_ml, fm2b_ml, fm3a_ml, fm3b_ml)
saveRDS(model_list, "Data/105_model_list.rds")

# largish - 7.5 MB  
model_list_brm <- list(brm_3a, brm_3c, brm_3c)
saveRDS(model_list_brm, "Data/105_model_list_brm.rds")

model_predictions <- list(newdat, pred_3a, pred_3b)
saveRDS(model_predictions, "Data/105_model_predictions.rds")

```

