---
title: "120 Initial analyses"
author: "DHJ"
date: "6 5 2020"
output: html_document
---

## 1. Libraries  
```{r, message=FALSE, warning=FALSE, results='hide'}

library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(mgcv)
library(safejoin)

# devtools::install_github("lenz99-/lme4cens")
library(lme4cens)


```

### Function  
```{r}

#
# Make new variable 'VALUE_WW_r' with random values between
# 0.5*LOQ and LOQ for data undcer LOQ
#
# Returns data set
#
add_random_data <- function(data){
  
  # Set todata frame (not tibble)
  data <- as.data.frame(data)
  
  # Under LOQs
  sel <- !is.na(data$FLAG1)
  
  # Test that runif works for vactors of min, max:
  # runif(2, min = c(1,50), max = c(10,100))
  data$VALUE_WW_r <- data$VALUE_WW
  data$VALUE_WW_r[sel] <- runif(
    n = sum(sel), 
    min = data$LOQ[sel]/2,
    max = data$VALUE_WW[sel]
  )
  
  data
  
}

```


## 2. Data   
Note that we get stations from script 103  
```{r}

dat <- readRDS("Data/101_Selected_data.rds")
df_stations <- readRDS("Data/103_Selected_stations.rds")

df_parameter_groups <- read.csv2("Input_data/47_df_par.csv", stringsAsFactors = FALSE)



# xtabs(~STATION_CODE, df_stations ) %>% sort()
df_stations <- df_stations %>%
  mutate(MSTAT = case_when(
    STATION_CODE %in% "I969" ~ "RH",
    TRUE ~ MSTAT)) %>%
  group_by(STATION_CODE, MSTAT) %>%
  summarise_at(vars("Lat", "Lon", "Dist_along_coast"), mean)

check <- df_stations %>%
  group_by(STATION_CODE) %>%
  mutate(n = n()) %>%
  filter(n > 1)

if (nrow(check) > 0){
  cat("Some stations have >1 MSTAT codes - check 'check'! \n")
}
  
```

### Combine data  
```{r}

# Median LOQ (per year and tissue only - should be the same for all stations)
dat_param_loq <- dat %>%
  filter(!is.na(FLAG1)) %>%
  group_by(PARAM, MYEAR, TISSUE_NAME) %>%
  summarise(LOQ = median(VALUE_WW))

dat2 <- dat %>%
  safe_left_join(df_stations %>% select(STATION_CODE, Lat, Lon, Dist_along_coast, MSTAT), 
                 check = "CV",
                 by = "STATION_CODE") %>%
  safe_left_join(dat_param_loq, 
                 check = "CV",
                 by = c("PARAM", "MYEAR", "TISSUE_NAME")) %>%
  mutate(MSTAT = factor(MSTAT,  levels = c("IH", "RH", "B")))

```

### Use correct basis  
```{r}

pah <- c("ACNLE", "ACNE", "FLE", "PA", "ANT", "FLU", "PYR", "BAA", 
         "CHR", "BBJF", "BKF", "BAP", "DBA3A", "BGHIP", "ICDP", "NAP", 
         "BBJKF", "BJKF", "PAH16", "KPAH", "P_S") 
pfas <- c("PFOS", "PFOSA", "PFBS", "PFDcA", "PFHxA", "PFHxS", 
          "PFHpA", "PFUdA", "PFOA", "PFNA", "PFUdA")
metals <- c("AG", "AS", "CD", "CO", "CR", "CU", "HG", "SN", 
            "NI", "PB", "ZN")

dat2 <- dat2 %>%
  mutate(CONC = case_when(
    PARAM %in% c(pah, pfas, metals) ~ VALUE_DW,
    !PARAM %in% c(pah, pfas, metals) ~ VALUE_WW
  ),
  Basis = case_when(
    PARAM %in% c(pah, pfas, metals) ~ "Dry weight",
    !PARAM %in% c(pah, pfas, metals) ~ "Wet weight"
  )
  )
  
table(dat2$Basis)

```

## 3. Single parameter, with long-lat  

### Data
```{r}

param <- "CD"
tissue <- "Lever"

dat_param <- dat2 %>%
  filter(PARAM %in% param & TISSUE_NAME %in% tissue) %>%
  add_random_data() %>%
  mutate(log_CONC = log10(CONC))

```


### Mod 1a
```{r}

mod <- gam(log_CONC ~ te(Lon, Lat) + s(MYEAR), data = dat_param)

summary(mod)

plot(mod)

visreg::visreg2d(mod, "Lon", "Lat") 

```

### Mod 1b   
LAtitude only
```{r}

mod <- gam(FAT_PERC ~ te(Lat) + s(MYEAR), data = dat_param)

summary(mod)

visreg::visreg(mod)

dat_param$log_CONC <- log10(dat_param$VALUE_WW_r)

```

### Mod 2  
Lon-lat plus several things   
```{r}

mod <- gam(log_CONC ~ te(Lon, Lat) + s(MYEAR) + s(LNMEA) + s(FAT_PERC) , data = dat_param)

summary(mod)

plot(mod)

visreg::visreg2d(mod, "Lon", "Lat")


```

## 4. Test: dist_along_coast, adjust separetely for each station     
- First adjust for lenrgth and fat, separately for each station  
- Then analyse the adjusted values by year and distance along coast  
- Test for one series

### Data
```{r}

param <- "CD"
tissue <- "Lever"
# tissue <- "Whole soft body"

dat_param <- dat2 %>%
  filter(PARAM %in% param & TISSUE_NAME %in% tissue) %>%
  add_random_data() %>%
  mutate(log_CONC = log10(VALUE_WW)) %>%
  select(STATION_CODE, TISSUE_NAME, MSTAT, log_CONC, MYEAR, Dist_along_coast, LNMEA, FAT_PERC) %>%
  filter(complete.cases(.))

complete.cases(dat_param) %>% mean()
  
```

### Check data patterns  
```{r}

df_summ <- dat2 %>%
  filter(PARAM %in% param & TISSUE_NAME %in% tissue) %>%
  group_by(STATION_CODE, MYEAR) %>%
  summarise(n = n(), median = median(VALUE_WW), below_loq = mean(!is.na(FLAG1)), loq = mean(LOQ)) 

ggplot(df_summ, aes(MYEAR, STATION_CODE)) +
  geom_tile(aes(fill = n))

ggplot(df_summ, aes(MYEAR, STATION_CODE)) +
  geom_tile(aes(fill = below_loq))

ggplot(df_summ, aes(MYEAR, STATION_CODE)) +
  geom_tile(aes(fill = loq))

```



### Ordinary (pseudoreplicated) GAM
```{r}

mod <- gam(log_CONC ~ s(Dist_along_coast) + s(MYEAR) + s(LNMEA) + s(FAT_PERC) , 
           data = dat_param)

summary(mod)

```

### Adjust for length and fat (LF), functions  

Function 1 - to use for each station  
```{r, fig.height=3, fig.width=9}

# Use this function for each station
# Adds log_CONC_adj to the data
add_adjusted_value_LF_station <- function(data, LNMEA_mean, FAT_PERC_mean,
                                       plot = FALSE){
  no_years <- data$MYEAR %>% unique() %>% length()
  # MAke model
  if (no_years > 1){   # Check if several years for this station; if not, no need to adjust for year
    data$fMYEAR <- factor(data$MYEAR)
    mod <- lm(log_CONC  ~ LNMEA + FAT_PERC + fMYEAR, data = data)
  } else {
    mod <- lm(log_CONC  ~ LNMEA + FAT_PERC, data = data)
  }
  if (plot){
    par(mfrow = c(1,3), mar = c(4,5,2,1))
    visreg::visreg(mod)
  }
  pred_data <- data
  n <- nrow(data)
  pred_data$LNMEA <- rep(LNMEA_mean, n)
  pred_data$FAT_PERC <- rep(FAT_PERC_mean, n)
  pred <- predict(mod, pred_data)
  data$log_CONC_adj <- pred + residuals(mod)
  # remove fMYEAR, if needed
  if (no_years > 1){
    result <- as.data.frame(data %>% select(-fMYEAR))
  } else {
    result <- as.data.frame(data)
  }
  result
}

stations <- unique(dat_param$STATION_CODE)

# debugonce(add_adjusted_value_LF_station)
test_LF <- add_adjusted_value_LF_station(
  dat_param %>% filter(STATION_CODE == stations[1]),
  mean(dat_param$LNMEA, na.rm = TRUE),
  mean(dat_param$FAT_PERC, na.rm = TRUE),
  plot = TRUE
)

if (FALSE){
  for (i in seq_along(stations)){
    
    test <- add_adjusted_value_LF_station(
      dat_param %>% filter(STATION_CODE == stations[i]),
      mean(dat_param$LNMEA, na.rm = TRUE),
      mean(dat_param$FAT_PERC, na.rm = TRUE),
      plot = TRUE
    )
    
  }
}

if (FALSE){

  ggplot(test, aes(log_CONC, log_CONC_adj)) +
    geom_point()
  
  ggplot(test, aes(log_CONC_adj - log_CONC, LNMEA)) +
    geom_point()
  
  ggplot(test, aes(log_CONC_adj - log_CONC, FAT_PERC)) +
    geom_point()
  
}

```


Function 2 - perform function 1 for all stations    
All stations with at least 3 measurements   
```{r, fig.height=3, fig.width=9}

add_adjusted_value_LF <- function(data, plot = FALSE){
  
  if (data$TISSUE_NAME[1] == "Whole soft body"){
    result <- data %>%
      mutate(log_CONC_adj = log_CONC)
  } else {
    
    LNMEA_mean <- mean(data$LNMEA, na.rm = TRUE)
    FAT_PERC_mean <- mean(data$FAT_PERC, na.rm = TRUE)
    
    # Keep all stations with at least 5 measurements
    tab <- table(data$STATION_CODE)
    stations <- names(tab[tab >= 5])
    
    result <- stations %>%
      map_dfr(
        function(station)
          add_adjusted_value_LF_station(
            data %>% filter(STATION_CODE == station), 
            LNMEA_mean, FAT_PERC_mean, plot = plot) 
      )
  }
  result
}

# debugonce(add_adjusted_value_LF)
dat_param2a <- add_adjusted_value_LF(dat_param)

if (FALSE){


  test <- add_adjusted_value_LF(dat_param, plot = TRUE)
 
  ggplot(test, aes(log_CONC, log_CONC_adj)) +
    geom_point()
  
  ggplot(test, aes(log_CONC_adj - log_CONC, LNMEA)) +
    geom_point()
  
  ggplot(test, aes(log_CONC_adj - log_CONC, FAT_PERC)) +
    geom_point()
  
}

```



### Adjust for length only (L), functions  

Function 1 - to use for each station  
```{r, fig.height=3, fig.width=9}

# Use this function for each station
# Adds log_CONC_adj to the data
add_adjusted_value_L_station <- function(data, LNMEA_mean, 
                                       plot = FALSE){
  data$fMYEAR <- factor(data$MYEAR)
  mod <- lm(log_CONC  ~ LNMEA + fMYEAR, data = data)
  if (plot){
    par(mfrow = c(1,3), mar = c(4,5,2,1))
    visreg::visreg(mod)
  }
  pred_data <- data
  n <- nrow(data)
  pred_data$LNMEA <- rep(LNMEA_mean, n)
  pred <- predict(mod, pred_data)
  data$log_CONC_adj <- pred + residuals(mod)
  as.data.frame(data %>% select(-fMYEAR))

}

stations <- unique(dat_param$STATION_CODE)

# debugonce(add_adjusted_value_L_station)
test_L <- add_adjusted_value_L_station(
  dat_param %>% filter(STATION_CODE == stations[1]),
  mean(dat_param$LNMEA, na.rm = TRUE),
  plot = TRUE
)

if (FALSE){
  for (i in seq_along(stations)){
    
    test <- add_adjusted_value_L_station(
      dat_param %>% filter(STATION_CODE == stations[i]),
      mean(dat_param$LNMEA, na.rm = TRUE),
      mean(dat_param$FAT_PERC, na.rm = TRUE),
      plot = TRUE
    )
    
  }
}

if (FALSE){

  ggplot(test, aes(log_CONC, log_CONC_adj)) +
    geom_point()
  
  ggplot(test, aes(log_CONC_adj - log_CONC, LNMEA)) +
    geom_point()
  
  ggplot(test, aes(log_CONC_adj - log_CONC, FAT_PERC)) +
    geom_point()
  
}

```


Function 2 - perform function 1 for all stations    
```{r, fig.height=3, fig.width=9}

add_adjusted_value_L <- function(data, plot = FALSE){
  
  if (data$TISSUE_NAME[1] == "Whole soft body"){
    result <- data %>%
      mutate(log_CONC_adj = log_CONC)
  } else {
    
    LNMEA_mean <- mean(data$LNMEA, na.rm = TRUE)

    # Keep all stations with at least 5 measurements
    tab <- table(data$STATION_CODE)
    stations <- names(tab[tab >= 5])
    
    result <- stations %>%
      map_dfr(
        function(station)
          add_adjusted_value_L_station(
            data %>% filter(STATION_CODE == station), 
            LNMEA_mean, plot = plot) 
      )
  }
  result
}

# debugonce(add_adjusted_value_L)
dat_param2b <- add_adjusted_value_L(dat_param)

if (FALSE){


  test <- add_adjusted_value_L(dat_param, plot = TRUE)
 
  ggplot(test, aes(log_CONC, log_CONC_adj)) +
    geom_point()
  
  ggplot(test, aes(log_CONC_adj - log_CONC, LNMEA)) +
    geom_point()
  
  ggplot(test, aes(log_CONC_adj - log_CONC, FAT_PERC)) +
    geom_point()
  
}

```



### Linear analysis by year and dist. along coast   
Use gls with AR1 model  
```{r}

dat_param3 <- dat_param2a %>%
  select(STATION_CODE, log_CONC_adj, MYEAR, Dist_along_coast) %>%
  filter(complete.cases(.))  # %>%
  # group_by(STATION_CODE, MYEAR, Dist_along_coast) %>%
  # summarize(log_CONC_adj = mean(log_CONC_adj))

complete.cases(dat_param3) %>% mean()

# PSeudorepl
mod0 <- gls(log_CONC_adj ~ MYEAR + Dist_along_coast, data = dat_param3)
acf(residuals(mod0), type = "partial")

mod10 <- gls(log_CONC_adj ~ 1, data = dat_param3,
            correlation = corAR1(form = ~1 | STATION_CODE))
mod1a <- gls(log_CONC_adj ~ MYEAR, data = dat_param3,
            correlation = corAR1(form = ~1 | STATION_CODE))
mod1b <- gls(log_CONC_adj ~ Dist_along_coast, data = dat_param3,
            correlation = corAR1(form = ~1 | STATION_CODE))

mod1c <- gls(log_CONC_adj ~ MYEAR + Dist_along_coast, data = dat_param3,
            correlation = corAR1(form = ~1 | STATION_CODE))

mod1d <- gls(log_CONC_adj ~ MYEAR*Dist_along_coast, data = dat_param3,
            correlation = corAR1(form = ~1 | STATION_CODE))

aic <- AIC(mod0, mod10, mod1a, mod1b, mod1c, mod1d)
aic$dAIC <- aic$AIC - min(aic$AIC)
aic

# AIC wanrs that "models are not all fitted to the same number of observations"
# BUT they all have:
list(mod0, mod10, mod1a, mod1b, mod1c, mod1d) %>% map_int(~summary(.)$dims$N)

# summary(mod1d) %>% str()
summary(mod1a)$tTable

# summary(mod1d)$tTable
# summary(mod1c)$tTable
# summary(mod1c)$tTable
# summary(mod1c)$tTable[2:3,] %>% matrix(nrow = 1) %>% data.frame()


```

### Linear analysis, function    
```{r}

run_gls <- function(data){
  
  data <- data %>%
    select(STATION_CODE, log_CONC_adj, MYEAR, Dist_along_coast) %>%
    filter(complete.cases(.))  # %>%
  # group_by(STATION_CODE, MYEAR, Dist_along_coast) %>%
  # summarize(log_CONC_adj = mean(log_CONC_adj))
  
  mod10 <- gls(log_CONC_adj ~ 1, data = data,
               correlation = corAR1(form = ~1 | STATION_CODE))
  mod1a <- gls(log_CONC_adj ~ MYEAR, data = data,
               correlation = corAR1(form = ~1 | STATION_CODE))
  mod1b <- gls(log_CONC_adj ~ Dist_along_coast, data = data,
               correlation = corAR1(form = ~1 | STATION_CODE))
  mod1c <- gls(log_CONC_adj ~ MYEAR + Dist_along_coast, data = data,
               correlation = corAR1(form = ~1 | STATION_CODE))
  mod1d <- gls(log_CONC_adj ~ MYEAR*Dist_along_coast, data = data,
               correlation = corAR1(form = ~1 | STATION_CODE))
  
  aic <- AIC(mod10, mod1a, mod1b, mod1c, mod1d)
  aic$dAIC <- aic$AIC - min(aic$AIC)
  
  best_model <- which.min(aic$AIC)
  
  result_values <- summary(mod1c)$tTable[2:3,] %>% as.numeric()
  result <- c(best_model, result_values) %>% matrix(nrow = 1) %>% data.frame()
  names(result) <- c("Best_model",
                     "Year_est", "Position_est",
                     "Year_se", "Position_se",
                     "Year_t", "Position_t",
                     "Year_p", "Position_p")
  result
}

# debugonce(run_gls)
run_gls(dat_param2a)

```

### Function for the whole thing, one replicate      
```{r}

analysis_one_par_one_repl <- function(param, tissue, data){

  # Select data
  data_selected <- data %>%
    filter(PARAM %in% param & TISSUE_NAME %in% tissue) %>%
    add_random_data() %>%
    mutate(log_CONC = log10(VALUE_WW_r)) %>%
    select(STATION_CODE, TISSUE_NAME, log_CONC, MYEAR, Dist_along_coast, LNMEA, FAT_PERC) %>%
    filter(complete.cases(.))
  
  stations <- unique(data_selected$STATION_CODE)
  
  # Add adjusted value
  if (tissue %in% "Whole soft body"){
    data_selected <- add_adjusted_value_L(data_selected)
  } else {
    data_selected <- add_adjusted_value_LF(data_selected)
  }
  
  # Run analysis
  result <- run_gls(data_selected)
  data.frame(PARAM = param, TISSUE_NAME = tissue, result,
             stringsAsFactors = FALSE)
  
}

# Testing 
analysis_one_par_one_repl("CD", "Lever", dat2)
# analysis_one_par_one_repl("CD", "Whole soft body", dat2)
# debugonce(analysis_one_par_one_repl)
# debugonce(add_adjusted_value_LF)
# analysis_one_par_one_repl("HG", "Muskel", dat2)

# 1:5 %>% set_names()
```
```{r}

1:3 %>% 
  set_names() %>% 
  map_dfr(
  ~analysis_one_par_one_repl(param = "CD", 
                             tissue = "Lever", 
                             data = dat2),
  .id = "Repl"
)


```

### Function for the whole thing, n replicates  
Replicates needed since 'add_random_data' will give different results each time  
```{r}

analysis_one_par <- function(param, tissue, data, nrepl = 5){
  
  seq(1, nrepl) %>%
    set_names() %>%
    map_dfr(
      ~analysis_one_par_one_repl(param = param, 
                                 tissue = tissue, 
                                 data = data),
      .id = "Repl")
  
}


analysis_one_par("CD", "Lever", dat2)
analysis_one_par("HG", "Muskel", dat2, nrepl = 2)


```

## 5. Run for all parameters + tissues


### Number of data   
Naturally higher for cod than for blue mussel
```{r}

dat2 %>%
  count(PARAM, TISSUE_NAME) %>%
  ggplot(aes(n)) + 
  geom_histogram(binwidth = 200) +
  facet_wrap(vars(TISSUE_NAME))

dat2 %>%
  count(PARAM, TISSUE_NAME) %>% 
  ggplot(aes(n)) + 
  geom_histogram(binwidth = 25) +
  facet_wrap(vars(TISSUE_NAME)) +
  coord_cartesian(xlim = c(0,500))

```

### Number of stations 
```{r}
# Number of stations 
df_acceptable_stations <- dat2 %>%
  count(PARAM, TISSUE_NAME, STATION_CODE, MSTAT, Lat, MYEAR) %>%
  filter(n >= 3) %>%  # min. number of samples per station/year 
  count(PARAM, TISSUE_NAME, STATION_CODE, MSTAT, Lat) %>%
  filter(n >= 3)      # min. number of samples per station/year

ggplot(df_acceptable_stations, aes(Lat, fill = MSTAT)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(vars(TISSUE_NAME))

df_param <- df_acceptable_stations %>%
  mutate(Area = case_when(
    Lat > 65 ~ "North",
    Lat > 63 ~ "Mid",
    TRUE ~ "South"
  ),
  Impacted = (MSTAT == "IH")
  ) %>% 
  arrange(PARAM, TISSUE_NAME, Area) %>%
  count(PARAM, TISSUE_NAME, Area, Impacted)

df_param_all <- df_param %>%
  group_by(PARAM, TISSUE_NAME, Area) %>% 
  summarise(n = sum(n)) %>%
  ungroup() %>%
  tidyr::pivot_wider(names_from = "Area", values_from = "n") 

df_param_notimpacted <- df_param %>%
  filter(!Impacted) %>%
  tidyr::pivot_wider(names_from = "Area", values_from = "n") %>%
  select(-Impacted)

df1 <- df_param_all %>%
  mutate(Spatial_coverage = case_when(
    North >= 2 ~ "OK",
    TRUE ~ "Not OK")) %>%
  count(TISSUE_NAME, Spatial_coverage) %>% # View()
  rename(All = n)

df2 <- df_param_notimpacted %>%
  mutate(Spatial_coverage = case_when(
    North >= 2 ~ "OK",
    TRUE ~ "Not OK")) %>% # View()
  count(TISSUE_NAME, Spatial_coverage) %>%
  rename(Notimpacted = n) 

left_join(df1, df2, by = c("TISSUE_NAME", "Spatial_coverage"))

```

### Select time series  
Bsed on 'df_param_notimpacted'  
```{r}

dat_param_tissue <- dat2 %>%
  distinct(PARAM, TISSUE_NAME) %>%
  # Only difference from the next: using 'df_param_notimpacted' here:
  left_join(df_param_notimpacted, by = c("PARAM", "TISSUE_NAME")) %>%
  filter(North >= 2) %>% 
  as.data.frame()

# head(dat_param_tissue)  
nrow(dat_param_tissue)  
```

Safe version of analysis_one_par  
```{r}
analysis_one_par_s <- safely(analysis_one_par)
```


### Analysis - Not impacted stations  
```{r, warning=FALSE, message=FALSE}

dat_param_tissue_notimpacted <- dat2 %>%
  distinct(PARAM, TISSUE_NAME) %>%
  # Only difference from the next: using 'df_param_notimpacted' here:
  left_join(df_param_notimpacted, by = c("PARAM", "TISSUE_NAME")) %>%
  filter(North >= 2) %>% 
  as.data.frame()

nrow(dat_param_tissue_notimpacted)

dat2_notimpacted <- dat2 %>%
  # Only difference from the next: using 'df_param_notimpacted' here:
  filter(!MSTAT %in% "IH") %>% 
  as.data.frame()


t0 <- Sys.time()
result_list_notimpacted <- seq(1:nrow(dat_param_tissue)) %>%
# result_list <- seq(1,10) %>%
  map(
    ~analysis_one_par_s(dat_param_tissue$PARAM[.], 
                        dat_param_tissue$TISSUE_NAME[.], 
                        dat2_notimpacted,    # NOTE
                        nrepl = 3)
  )
t1 <- Sys.time()
t1-t0


saveRDS(result_list_notimpacted, "Data/120_result_list_notimpacted.rds")

```

### Analysis - all stations  
```{r, warning=FALSE, message=FALSE}

dat_param_tissue_allstations <- dat2 %>%
  distinct(PARAM, TISSUE_NAME) %>%
  # Only difference from the next: using 'df_param_notimpacted' here:
  left_join(df_param_all, by = c("PARAM", "TISSUE_NAME")) %>%
  filter(North >= 2) %>% 
  as.data.frame()
nrow(dat_param_tissue_allstations)

t0 <- Sys.time()
result_list_allstations <- seq(1:nrow(dat_param_tissue)) %>%
# result_list <- seq(1,10) %>%
  map(
    ~analysis_one_par_s(dat_param_tissue$PARAM[.], 
                        dat_param_tissue$TISSUE_NAME[.], 
                        dat2,
                        nrepl = 3)
  )
t1 <- Sys.time()
t1-t0


saveRDS(result_list_allstations, "Data/120_result_list_allstations.rds")

```




### Load, if needed 
```{r}

# result_list_allstations <- readRDS("Data/120_result_list_allstations.rds")
# result_list_notimpacted <- readRDS("Data/120_result_list_notimpacted.rds")

```

### Extract coefficients, function

```{r}

get_coefficients <- function(result_list, parameter_groups = df_parameter_groups){
  
  # Transpose result list (so results are list part [[1]] and errors are list part [[2]])
  result_list <- purrr::transpose(result_list)
  
  #### Make data frame (result)

  ok <- result_list[[2]] %>% map_lgl(is.null)
  sum(ok)
  
  result <- result_list[[1]][ok] %>% 
    bind_rows()
  
  #### Met mean coefficients from model
  
  result_coef <- result %>%
    group_by(PARAM, TISSUE_NAME) %>%
    summarise_at(vars(Year_est:Position_t), mean, na.rm = TRUE) %>%
    ungroup()
  
  #### Sort order
  
  group_order <- c("Metals and metalloids", "Chlorobiphenyls", "Polycyclic aromatic hydrocarbons (PAHs)",
                   "Organobromines", "Organochlorines (general)", "Organofluorines",
                   "Phosphorus flame retardant (PFR)",
                   "Chlorinated paraffins", "Dichloro-diphenyl-trichloroethane (DDTs)", 
                   "Hexachlorocyclohexanes", "Others"  
  )
  
  result_coef <- result_coef %>%
    left_join(parameter_groups %>% select(Parameter.Code, Substance.Group),
              by = c("PARAM" = "Parameter.Code"))
  
  # Add some parameters that are lacking
  result_coef <- result_coef %>%
    mutate(Substance.Group = case_when(
      PARAM %in% c("MCCP eksl. LOQ", "MCCP eksl. LOQ") ~ "Chlorinated paraffins",
      PARAM %in% c("KPAH", "PAH16") ~ "Polycyclic aromatic hydrocarbons (PAHs)",
      PARAM %in% "Sum HBCD" ~ "Organobromines",
      is.na(Substance.Group) ~ "Others",
      TRUE ~ Substance.Group
    )) %>%
    mutate(Substance.Group = factor(Substance.Group, levels = group_order)) %>%
    arrange(Substance.Group) %>%
    mutate(PARAM = forcats::fct_inorder(PARAM))
  
  if (FALSE){
    result_coef %>% select(PARAM, Substance.Group)
  }
  
  result_coef
  
}

# debugonce(get_coefficients)
# result_coef_notimpacted <- get_coefficients(result_list_notimpacted)

```


### Plot liver results  
```{r, fig.width=10, fig.height=6}

result_coef_notimpacted <- get_coefficients(result_list_notimpacted)

gg <- result_coef_notimpacted %>%
  filter(TISSUE_NAME %in% "Lever") %>%
  ggplot(aes(PARAM, Position_est)) +
  geom_point() +
  geom_pointrange(aes(ymin = Position_est - 2*Position_se,
                      ymax = Position_est + 2*Position_se)) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0),
        plot.margin = margin(6, 45, 6, 6)) +
  geom_hline(yintercept = 0) +
  labs(title = "Concentrations along coast - not impacted stations -  fish liver", 
       ylab = "Effect of position along coast")
    
ggsave("Figures/120_Coasteffect_notimpaced_liver.png", gg, width = 12, height = 6)

gg

```

#### Plot muscle results  
```{r, fig.width=10, fig.height=6}

gg <- result_coef_notimpacted %>%
  filter(TISSUE_NAME %in% "Muskel") %>%
  ggplot(aes(PARAM, Position_est)) +
  geom_point() +
  geom_pointrange(aes(ymin = Position_est - 2*Position_se,
                      ymax = Position_est + 2*Position_se)) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0),
        plot.margin = margin(6, 45, 6, 6)) +
  geom_hline(yintercept = 0) +
  labs(title = "Concentrations along coast - not impacted stations - fish muscle", 
       ylab = "Effect of position along coast")
    
ggsave("Figures/120_Coasteffect_notimpaced_muscle.png", gg, width = 12, height = 6)

gg

```

#### Plot blue mussel results  
```{r, fig.width=10, fig.height=6}

gg <- result_coef_notimpacted %>%
  filter(TISSUE_NAME %in% "Whole soft body") %>%
  ggplot(aes(PARAM, Position_est)) +
  geom_point() +
  geom_pointrange(aes(ymin = Position_est - 2*Position_se,
                      ymax = Position_est + 2*Position_se)) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0),
        plot.margin = margin(6, 45, 6, 6)) +
  geom_hline(yintercept = 0) +
  labs(title = "Concentrations along coast - not impacted stations - blue mussels", 
       ylab = "Effect of position along coast")
    
ggsave("Figures/120_Coasteffect_notimpaced_mussel.png", gg, width = 12, height = 6)

gg

```
#### Soft tissue (blue mussel)
```{r, fig.width=9, fig.height=6}
result_coef %>%
  filter(TISSUE_NAME %in% "Whole soft body") %>%
  ggplot(aes(PARAM, Position_est)) +
  geom_point() +
  geom_pointrange(aes(ymin = Position_est - 2*Position_se,
                      ymax = Position_est + 2*Position_se)) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0)) +
  geom_hline(yintercept = 0)
    

```

#### Muscle
```{r, fig.width=9, fig.height=6}
result_coef %>%
  filter(TISSUE_NAME %in% "Muskel") %>%
  ggplot(aes(PARAM, Position_est)) +
  geom_point() +
  geom_pointrange(aes(ymin = Position_est - 2*Position_se,
                      ymax = Position_est + 2*Position_se)) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0)) +
  geom_hline(yintercept = 0)
    

```


```{r, fig.width=9, fig.height=6}

result_coef <- result %>%
  group_by(PARAM, TISSUE_NAME) %>%
  summarise_all(mean) %>%
  filter(TISSUE_NAME %in% "Whole soft body")

ggplot(result_coef, aes(PARAM, Position_est)) +
  geom_point() +
  geom_pointrange(aes(ymin = Position_est - 2*Position_se,
                      ymax = Position_est + 2*Position_se)) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0)) +
  geom_hline(yintercept = 0)
  
  

```



```{r}

ggplot(result_coef, aes(PARAM, Position_est)) +
  geom_point() +
  geom_pointrange(aes(ymin = Year_est - 2*Year_se,
                      ymax = Year_est + 2*Year_se)) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0)) +
  geom_hline(yintercept = 0)
  

```

