---
title: "121 Analysis 01"
author: "DHJ"
date: "6 5 2020"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true 
---

Based on script 120   


## 1. Libraries  
```{r, message=FALSE, warning=FALSE, results='hide'}


library(rlang)

library(devtools)
library(lme4)
library(usethis)
library(dplyr)
library(tidyr)
library(purrr)
library(forcats)
library(ggplot2)
library(mgcv)
library(visreg)

# devtools::install_github("moodymudskipper/safejoin")
library(safejoin)

# devtools::install_github("lenz99-/lme4cens")
library(lme4cens)

# For SpatialPoints() function in part 2, used for map in part 8
library(sp)

# For combining plots
library(cowplot)

# For nicer tables
library(knitr)
library(kableExtra)

# For get_point_on_coastline()
# Used in part 8  
source("103_Distance_along_coast_functions.R")

```


## 2. Data   
Note that we get stations from script 103  
```{r}
# Data including trophic level
dat <- readRDS("Data/104_Selected_data.rds")

# Extra isotope data
dat_isotopes <- readRDS("Input_data/87_df_isotopes.rds")

# Station metadata
df_stations <- readRDS("Data/103_Selected_stations.rds")




# xtabs(~STATION_CODE, df_stations ) %>% sort()
df_stations <- df_stations %>%
  mutate(MSTAT = case_when(
    STATION_CODE %in% "I969" ~ "RH",
    TRUE ~ MSTAT)) %>%
  group_by(STATION_CODE, MSTAT) %>%
  summarise_at(vars("Lat", "Lon", "Dist_along_coast"), mean)

check <- df_stations %>%
  group_by(STATION_CODE) %>%
  mutate(n = n()) %>%
  filter(n > 1)

if (nrow(check) > 0){
  cat("Some stations have >1 MSTAT codes - check 'check'! \n")
}
  
```

## 3. GAMM results  
```{r}

# Use the saved results
gamm_list <- readRDS("Data/120_gamm_list_notimpacted.rds")

```



## 4. Check GAMM results  

### Get analyses that didn't fail  

```{r}

cat("Number of regressions that worked (numbers / fraction): \n")
ok <- gamm_list[["error"]] %>% map_lgl(is.null)
sum(ok)
mean(ok)  # 0.96

# Save "ok" in data frame used to run analysis
listno_replicate$Result_ok <- ok

```

### Extract t-values and plot values (fitted lines)  
- t-values: ttable_gamm  
- Also take the median fitted lines (across replicates): plotvalues_gamm_med     
- Also add 'Substance.Group' for both    
```{r, warning=FALSE, results='hide', message=FALSE}

# Extract the one-line t-tables and combine
ttable_gamm <- gamm_list[["result"]][ok] %>% 
  map_df(~.[["ttable"]]) %>%
  # Add substance group
  left_join(df_parameter_groups[c("Parameter.Code", "Substance.Group")],
            by = c("PARAM" = "Parameter.Code"))

# Extract the line fits for the "Positopn" effects  
plotvalues_gamm <- gamm_list[["result"]][ok] %>% 
  map_df(~.[["plotvalues"]])

# Median fitted lines (across replicates)
plotvalues_gamm_med <- plotvalues_gamm %>%
  group_by(PARAM, TISSUE_NAME, Dist_along_coast) %>%
    summarise_at(
    vars(visregFit, visregLwr, visregUpr),
    median) %>%
  # Add substance group
  left_join(df_parameter_groups[c("Parameter.Code", "Substance.Group")],
            by = c("PARAM" = "Parameter.Code"))

# Check 'plotvalues_gamm' and 'plotvalues_gamm_med' for 
#   a parameter with many <LOQ values (BAP)
if (FALSE){
plotvalues_gamm %>%
  filter(PARAM == "BAP") %>%
  # We cheat a bit to recreate how Repl should actually be (because of code error; now fixed):
  mutate(Repl = rep(1:3, each = 101)) %>%   # xtabs(~TISSUE_NAME + Repl, .) 
  ggplot(aes(Dist_along_coast, visregFit)) + 
  geom_path(aes(color = factor(Repl)), size = 2) +
  geom_path(
    data = plotvalues_gamm_med %>% filter(PARAM == "BAP"),
    aes(Dist_along_coast, visregFit),
    linetype = 2
  )
}

```

### Check p-values and the fit's degrees of freedom    
- fit's degrees of freedom > 1 means non-linear fit  
```{r}

# All numbers are character, set to numeric
vars <- c("Repl", 
          "Year_edf", "Position_esdf", "Year_F", 
          "Position_F", "Year_p", "Position_p")
for (var in vars)
  ttable_gamm[[var]] <- as.numeric(ttable_gamm[[var]])

ttable_gamm %>%
  ggplot(aes(Position_p)) + geom_histogram()
ttable_gamm %>%
  ggplot(aes(Position_p, Position_esdf)) + geom_point()

ttable_gamm %>%
  xtabs(~(Position_p < 0.05) + (Position_esdf > 1), .)

ttable_gamm %>%
  xtabs(~ addNA(Substance.Group) + (Position_p < 0.05) + TISSUE_NAME, .)

# for checking
if (FALSE){
  ttable_gamm %>%
    filter(is.na(Substance.Group)) %>%
    xtabs(~PARAM, .) %>%
    names() %>%
    paste(collapse = ";")
}


```


## 5. Plot results with map   
Example: Organobromines   
- Pick only the most common ones, and those with a geographic pattern  
```{r}

plotgamm_group <- function(group = "Organobromines", minvalue = -0.8) {
  
  # Get positions for km's to show:
  points <- c(0, 500, 1000, 1500, 2000, 2500, 2685) %>% map_df(~get_point_on_coastline(.))
  
  if (!is.na(group)){
    pick_data <-plotvalues_gamm_med %>%
      # Pick data
      filter(grepl(group, Substance.Group,ignore.case = TRUE) &
               TISSUE_NAME %in% "Lever"
      )
    
  } else {
    pick_data <- plotvalues_gamm_med %>%
      filter(is.na(Substance.Group) &
               TISSUE_NAME %in% "Lever"
      )
    
  }
  
  gg1 <- pick_data %>% 
    # Add 'Position_p' (p-values) to data
    left_join(ttable_gamm %>% select(PARAM, TISSUE_NAME, Position_p), 
              by = c("PARAM", "TISSUE_NAME")) %>%
    mutate(Significant = ifelse(Position_p < 0.05, "Significant", "Not significant")) %>%
    # Find mean value (next 3 lines)
    group_by(PARAM) %>%
    mutate(mean_value = mean(visregFit)) %>%
    ungroup() %>%
    # Pick only the most common parameters (next 4 lines)
    filter(mean_value > minvalue & Significant == "Significant") %>%
    # Set factors in order following mean_value
    mutate(PARAM = forcats::fct_reorder(PARAM, mean_value, .desc = TRUE)) %>%
    # Plot
    ggplot(aes(Dist_along_coast, visregFit, color = PARAM)) + 
    geom_line(size = rel(1)) + 
    geom_vline(data = points, 
               aes(xintercept = distance),
               linetype = "dashed") +  
    annotate("vline", xintercept = points$distance) +
    labs(x = "Distance along coast", y = "log(Concentration in cod liver)") +
    theme_bw() 
  
  # Direction of text labels:
  points$Text_direction <- "West"
  points$Text_direction[c(1,6,7)] <- "East"
  
  # PLot
  gg2 <- ggplot(map_df, aes(x, y)) +
    geom_path() +
    coord_fixed() +
    geom_path(data = coast, color = "red") +
    geom_point(data = points, color = "blue") +
    geom_text(data = points %>% filter(Text_direction == "West"), 
              aes(x = x - 20000, label = paste(distance, "km")), 
              color = "blue", hjust = 1, size = rel(3)) +
    geom_text(data = points %>% filter(Text_direction == "East"), 
              aes(x = x + 20000, label = paste(distance, "km")), 
              color = "blue", hjust = 0, size = rel(3)) +
    expand_limits(x = c(min(map_df$x, na.rm = TRUE) - 150000,
                        max(map_df$x, na.rm = TRUE) + 200000)) +
    theme_minimal() +
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      panel.grid = element_blank()
    )
  
  cowplot::plot_grid(gg1, gg2, nrow = 1, rel_widths = c(2, 1))
  
}


```

### Plot a bunvh of groups  
```{r, fig.height=5, fig.width=9}

plotgamm_group("Organobromines")
plotgamm_group("Metals", minvalue = -2)
plotgamm_group("Chlorobiphenyls", minvalue = -1)
plotgamm_group("Paraffins", minvalue = 1)
plotgamm_group("DDT", minvalue = -1)
plotgamm_group("Organofluorines", minvalue = -2)
plotgamm_group("Phosphorus flame retardant", minvalue = -2)

plotgamm_group(NA, minvalue = -2)
  
```


## 9. Combine linear + non-linear results in table  

### Combine tables  
```{r, fig.width=9, fig.height=9}

# linear_results
tab1 <- linear_results %>%
  filter(TISSUE_NAME %in% "Lever" & !is.na(Position_est)) %>%
  select(PARAM, TISSUE_NAME, Position_est, Position_p) %>%
  group_by(PARAM, TISSUE_NAME) %>%
  summarise_all(list(min = min, mean = mean, median = median)) %>%
  ungroup() %>%
  mutate(Linear_effect = case_when(
    is.na(Position_est_mean) ~ "-",
    Position_est_mean < 0 ~ "Decreasing",
    Position_est_mean >= 0 ~ "Increasing"),
    Linear_p = case_when(
      is.na(Position_p_median) ~ "-",
      Position_p_median < 0.001 ~ "< 0.001",
      Position_p_median < 0.01 ~ round(Position_p_median, 3) %>% as.character(),
      Position_p_median <= 1 ~ round(Position_p_median, 2) %>% as.character()),
    Linear_p = cell_spec(
      Linear_p, "html", 
      color = ifelse(Position_p_median < 0.05, "red", "black"))
    ) %>% 
  select(PARAM, TISSUE_NAME, Linear_effect, Linear_p)

# tab1

# non-linear results
tab2 <- ttable_gamm %>%
  group_by(PARAM, TISSUE_NAME) %>%
  summarise_at(vars(Position_esdf, Position_p), median) %>%
  mutate(Non_linear_df = round(Position_esdf, 2), 
    Non_linear_p = case_when(
      is.na(Position_p) ~ "-",
      Position_p < 0.001 ~ "< 0.001",
      Position_p < 0.01 ~ round(Position_p, 3) %>% as.character(),
      Position_p <= 1 ~ round(Position_p, 2) %>% as.character()),
    Non_linear_p = cell_spec(
      Non_linear_p, "html", 
      color = ifelse(!is.na(Position_p) & Position_p < 0.05, "red", "black"))
    ) %>% 
  select(PARAM, TISSUE_NAME, Non_linear_df, Non_linear_p)

# Combine:
tab_comb <- left_join(tab1, tab2, by = c("PARAM", "TISSUE_NAME")) %>%
    # Add substance group
  left_join(df_parameter_groups[c("Parameter.Code", "Substance.Group")],
            by = c("PARAM" = "Parameter.Code")) %>%
  select(Substance.Group, everything()) %>%
  arrange(Substance.Group, PARAM) %>%
  mutate(
    Substance.Group = cell_spec(Substance.Group, "html", color = "black"),
        PARAM = cell_spec(PARAM, "html", color = "black"),
        TISSUE_NAME = cell_spec(TISSUE_NAME, "html", color = "black"),
        Linear_effect = cell_spec(Linear_effect, "html", color = "black"),
        Non_linear_df = cell_spec(Non_linear_df, "html", color = "black")
    )

```

### Order variables  
```{r}
sort_by_number <- function(x){
  number <- stringr::str_extract(x, "[0-9]+") %>% as.numeric()
  number[is.na(number)] <- 0
  order <- order(number)
  x[order]
}

move_to_back <- function(x, pattern){
  sel <- grepl(pattern, x)
  c(x[!sel], x[sel])
}
# move_behind(LETTERS, "B")

move_to_front <- function(x, pattern){
  sel <- grepl(pattern, x)
  c(x[sel], x[!sel])
}

pars_pcb <- tab_comb %>% 
  filter(Substance.Group %in% "Chlorobiphenyls") %>%
  pull(PARAM) %>%
  sort_by_number() %>%
  move_to_back("QCB")

pars_bde <- tab_comb$PARAM %>% grep("^BD", ., value = TRUE) %>%
  sort_by_number()

pars_hbcd <- tab_comb$PARAM %>% grep("HBCD", ., value = TRUE) %>%
  sort() %>%
  move_to_front("Sum HBCD")

pars_pfas <- tab_comb %>% 
  filter(Substance.Group %in% "Organofluorines") %>%
  pull(PARAM) %>% 
  move_to_front("PFAS$")  # since this is the sum  

# Show all, for check  
pars_pcb
pars_bde
pars_hbcd
pars_pfas

# Other parameters, in alphabetic order 
par_all <- tab_comb %>% pull(PARAM)
sel1 <- par_all %in% pars_pcb
sel2 <- par_all %in% pars_bde
sel3 <- par_all %in% pars_hbcd
sel4 <- par_all %in% pars_pfas
pars_other <- par_all[!(sel1 | sel2 | sel3 | sel4)]

# Correct order
par_levels <- c(pars_pcb, pars_bde, pars_hbcd, pars_pfas, pars_other)

# Set PARAM factor levels in correct order
tab_comb <- tab_comb %>%
  mutate(PARAM = factor(PARAM, levels = par_levels))

```

### Show table  
```{r, fig.width=11, fig.height=9}
kabletab <- kable(tab_comb %>% 
                    arrange(Substance.Group, PARAM),
                  format = "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = "condensed")

kabletab


#
# Tried to use pack_rows - gave up, perhaps retry later   
#
# for (category in group_order){
#   sel <- tab_comb$Substance.Group %in% category
#   if (sum(sel) > 0){
#     i <- which(sel) %>% range()
#     kabletab <- kabletab %>% pack_rows(category, i[1], i[2])
#   }
# }

```










