---
title: "121 Analysis 01"
author: "DHJ"
date: "6 5 2020"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true 
---

Based on script 120   


## 1. Libraries  
```{r, message=FALSE, warning=FALSE, results='hide'}


library(rlang)

library(devtools)
library(usethis)

library(dplyr)
library(tidyr)
library(purrr)
library(forcats)
library(ggplot2)
library(mgcv)
library(visreg)

# devtools::install_github("moodymudskipper/safejoin")
library(safejoin)

# devtools::install_github("lenz99-/lme4cens")
library(lme4cens)

# For SpatialPoints() function in part 2, used for map in part 8
library(sp)

# For combining plots
library(cowplot)

# For nicer tables
library(knitr)
library(kableExtra)

# For get_point_on_coastline()
# Used in part 8  
source("103_Distance_along_coast_functions.R")

```



### Functions   
- add_random_data  
    - Makes new variable 'VALUE_WW_r' with random values for data under LOQ  
- format_p
    - Formats p-values  

```{r}

#
# Make new variable 'VALUE_WW_r' with random values between
# 0.5*LOQ and LOQ for data undcer LOQ
#
# Returns data set
#
add_random_data <- function(data){
  
  # Set todata frame (not tibble)
  data <- as.data.frame(data)
  
  # Under LOQs
  sel <- !is.na(data$FLAG1)
  
  # Test that runif works for vactors of min, max:
  # runif(2, min = c(1,50), max = c(10,100))
  data$VALUE_WW_r <- data$VALUE_WW
  data$VALUE_WW_r[sel] <- runif(
    n = sum(sel), 
    min = data$LOQ[sel]/2,
    max = data$VALUE_WW[sel]
  )
  
  data
  
}


# Formats p-values
format_p <- function(p){
  case_when(
      p < 0.001 ~ "< 0.001",
      p < 0.01 ~ round(p, 3) %>% as.character(),
      p <= 1 ~ round(p, 2) %>% as.character()
      )
}
# format_p(0.0001)
# format_p(0.002334324)
# format_p(0.02334324)

```



## 2. Data   
Note that we get stations from script 103  
```{r}
# Data including trophic level
dat <- readRDS("Data/104_Selected_data.rds")

# "Input_data/"
# dat <- readRDS("Input_data/109_adjusted_data_2020-08-05.rds") %>%
#   filter(MYEAR >= 1994)


# Extra isotope data - not needed here
# dat_isotopes <- readRDS("Input_data/87_df_isotopes.rds")

# Station metadata
df_stations <- readRDS("Data/103_Selected_stations.rds")




# xtabs(~STATION_CODE, df_stations ) %>% sort()
df_stations <- df_stations %>%
  mutate(MSTAT = case_when(
    STATION_CODE %in% "I969" ~ "RH",
    TRUE ~ MSTAT)) %>%
  group_by(STATION_CODE, MSTAT) %>%
  summarise_at(vars("Lat", "Lon", "Dist_along_coast"), mean)

check <- df_stations %>%
  group_by(STATION_CODE) %>%
  mutate(n = n()) %>%
  filter(n > 1)

if (nrow(check) > 0){
  cat("Some stations have >1 MSTAT codes - check 'check'! \n")
}
  
```

#### Check  
```{r}

dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005) %>%
  xtabs(~STATION_CODE + MYEAR, .)


```
### Airport data  
```{r}

dat_airports <- readxl::read_excel("Input_data/Lufthavner Avinor koordinater utvidet.xlsx",
                                  range = cellranger::cell_cols(c("B", "C", "D"))) %>%
  rename(x = UTM_ost, 
         y = UTM_nord)

# dat_airports


```
#### Add long, lat to airport data  
```{r}
library(sp)

crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=33 +ellps=WGS84 +datum=WGS84 +units=m"
# note that you might want to change zone=32 to e.g. 33

SP.utm <- SpatialPoints(dat_airports[,c("x", "y")], 
                        proj4string=CRS(crs_utm)
                        )
SP.longlat <- spTransform(SP.utm, CRS(crs_longlat))

dat_airports <- dat_airports %>% 
  mutate(Lon = SP.longlat@coords[,1],
        Lat = SP.longlat@coords[,2]
  )

```


### dat2 - combined data  
Adding
- position data + MSTAT (type of station - industry-impacted, representative or background)  
- LOQ  
- mean trophic level per station  

```{r}


# Median LOQ (per year and tissue only - should be the same for all stations)
dat_param_loq <- dat %>%
  filter(!is.na(FLAG1)) %>%
  group_by(PARAM, MYEAR, TISSUE_NAME) %>%
  summarise(LOQ = median(VALUE_WW), .groups = "drop")

dat2 <- dat %>%
  ungroup() %>%
  # Add position data + MSTAT (type of station - industry-impacted, representative or background)
  safe_left_join(df_stations %>% 
                   select(STATION_CODE, Lat, Lon, Dist_along_coast, MSTAT),
                 check = "CV",
                 by = "STATION_CODE",
                 na_matches = "never") %>%
  # Add LOQ
  safe_left_join(dat_param_loq,
                 check = "CV",
                 by = c("PARAM", "MYEAR", "TISSUE_NAME"),
                 na_matches = "never") %>%
  mutate(MSTAT = factor(MSTAT,  levels = c("IH", "RH", "B"))) %>%
  # Add mean trophic level per station
  group_by(STATION_CODE) %>%
  mutate(TL_mean = mean(TL, na.rm = TRUE)) %>%
  ungroup() 

cat("'dat2' created. \n")

# dat2 <- dat

sel <- is.na(dat2$Lat)
dat2 <- dat2[!sel,]
cat(sum(sel), "lines without coordinates were deleted \n")

```

### Add UTM coordinates  
```{r}

SP <- SpatialPoints(dat2[, c("Lon", "Lat")],
                    proj4string=CRS(crs_longlat)
)
SP.UTM <- spTransform(SP, CRS(crs_utm))
# Add transformed coords to data set

dat2 <- dat2 %>%
  mutate(x = SP.UTM@coords[,1],
         y = SP.UTM@coords[,2])


```


### Test add_random_data() function   
Adds a new column 'VALUE_WW_r' which has random data 
```{r}

if (FALSE){
  # Check parameters with ca 50% under LOQ
  dat2 %>%
    filter(MYEAR > 2014) %>%
    group_by(PARAM) %>%
    summarise(less_thans = mean(!is.na(FLAG1))) %>%
    filter(less_thans < 0.5) %>%
    arrange(desc(less_thans))
}

# Just pick 10 randm PFUdA records
test <- dat2 %>%
  filter(PARAM %in% "PFUdA") %>%
  select(MYEAR, STATION_CODE, VALUE_WW, FLAG1, LOQ) %>%
  head(10)

test
# debugonce(add_random_data)
test %>% add_random_data()

```


### Use correct basis  
```{r}

pfas <- c("PFOS", "PFOSA", "PFBS", "PFDcA", "PFHxA", "PFHxS", 
          "PFHpA", "PFUdA", "PFOA", "PFNA", "PFUdA")

```


### Data for plotting maps  
Used in part 8  
```{r}
#
# Get Norway map data
#
test <- maps::map("world", "Norway", plot = FALSE)   # map data for Norway - this is just to get region names
sel <- grepl("Svalbard", test$names) | test$names == "Norway:Jan Mayen"  # select Svalbard + Jan Mayen
# test$names[!sel]
map <- maps::map("world", test$names[!sel], exact = TRUE, plot = FALSE)  # Norway w/o Svalbard + Jan Mayen
map_df <- data.frame(Longitude = map$x, Latitude = map$y)

#
# Add UTM coordinates (x and y) to map
#
coordinate_exists <- !is.na(map_df$Longitude)   # sp doesn't like NAs
SP <- sp::SpatialPoints(map_df[coordinate_exists, c("Longitude", "Latitude")],
                    proj4string=CRS(crs_longlat)
)
SP.UTM <- sp::spTransform(SP, CRS(crs_utm))
# Add transformed coords to data set
map_df$x[coordinate_exists] <- SP.UTM@coords[,1]
map_df$y[coordinate_exists] <- SP.UTM@coords[,2]


#
# "Coast" data (coordinates for segments along the coast)
#
coast <- readRDS("Data/102_coast_coordinates.rmd")

#
# Make 'coastsegment_distance'   
#
# Distances for start points of the coast segments
segment_dx <- diff(coast$x)/1000
segment_dy <- diff(coast$y)/1000
coastsegment_distance <- sqrt(segment_dx^2 + segment_dy^2) %>% cumsum()
coastsegment_distance <- c(0, coastsegment_distance)


```

## 3. dat_param - data for one parameter
```{r}

param <- "PFOS"

for ( tissue in c("Lever", "Whole soft body")){
   
   dat_param <-  dat2 %>%
     filter(PARAM %in% param & TISSUE_NAME %in% tissue) %>% 
     add_random_data() %>%
     mutate(log_CONC = log10(VALUE_WW)) %>%
     select(PARAM, STATION_CODE, TISSUE_NAME, MSTAT, log_CONC, MYEAR, Dist_along_coast, LNMEA, FAT_PERC, TL, TL_mean) # %>%
   
   cat("\n-----------------------------------------------------------\n")
   cat("Sample size (since 2000) for param:", param, "and tissue:", tissue, "\n")  
   dat_param %>%
     filter(MYEAR >= 2000) %>%
     xtabs(~STATION_CODE + MYEAR, .) %>%
     print()
   
 } 
 
 
# Check missing values per year



```
## 4. Map  

### a. Data
```{r}

if (FALSE){
  
  # PLot using lon, Lat
  df <- dat2 %>%
    filter(PARAM %in% param & TISSUE_NAME %in% "Lever") %>% 
    distinct(STATION_CODE, Lon, Lat, MYEAR) %>%
    count(STATION_CODE, Lon, Lat)
  
  ggplot(map_df, aes(Longitude, Latitude)) +
    geom_path() +
    coord_map("lambert", lat0 = 64, lon0 = 11) +
    geom_point(data = df, aes(Lon, Lat, fill = n), pch = 21, size = 3)
  
}

dat_stations <- dat2 %>%
  filter(PARAM %in% param & TISSUE_NAME %in% "Lever") %>% 
  distinct(STATION_CODE, x, y, MYEAR) %>%
  count(STATION_CODE, x, y)

ggplot(map_df, aes(x, y)) +
  geom_path() +
  coord_fixed() +
  geom_point(data = dat_stations, aes(fill = n), pch = 21, size = 3)


```


### b. Airports  
```{r}

ggplot(map_df, aes(x, y)) +
  geom_path() +
  coord_fixed() +
  geom_point(data = dat_airports, color = "red3")

```

## 5. Distance to closest airport    

### a. Functions
```{r}

# Get the n_closest airports to station no. 'i' in data frame 'data'
# Output: data frame with n_closest
get_closest <- function(i, data, airports, n_closest = 3){
  df <- as.data.frame(data)[i,]
  dx <- df$x - airports$x
  dy <- df$y - airports$y
  dist <- sqrt((dx^2) + (dy^2))/1000
  i_order <- order(dist)
  i_min <- i_order[1:n_closest]
  tibble(i = 1:n_closest,
         STATION_CODE = df$STATION_CODE, 
         x = df$x,
         y = df$y,
         Distance = dist[i_min],
         Airport = dat_airports[i_min,] %>% pull(LUFTHAVN),
         Airport_x = dat_airports[i_min,] %>% pull(x),
         Airport_y = dat_airports[i_min,] %>% pull(y)
  ) 
}

# TEST
if (FALSE)
  get_closest(1, dat_stations, dat_airports)


# As get_closest, but plots the n_closest airports   
plot_closest <- function(..., range = 200, print_plot = FALSE){
  
  
  df <- get_closest(...) %>%
    mutate(Label = paste(i, "-", Airport))
  
  ran <- range*1000
  
  gg <- ggplot(df, aes(Airport_x, Airport_y)) +
    geom_point() +
    geom_text(aes(x = Airport_x + 5000, label = Label), hjust = 0) +
    geom_point(data = df[1,], aes(x=x, y=y), color = "red2") +
    geom_path(data = map_df, aes(x=x, y=y)) +
    coord_fixed(
      xlim = df[1,]$x + c(-ran/2, ran/2), 
      ylim = df[1,]$y + c(-ran/2, ran/2)
    ) +
    theme(
      axis.title = element_blank(),
      axis.text = element_blank()
    ) +
    labs(title = df[1,]$STATION_CODE)
  
  if (print_plot)
    print(gg)
  
  invisible(gg)
}

if (FALSE)
  plot_closest(1, dat_stations, dat_airports, print_plot = TRUE)

```

### b, Plot all  
```{r, fig.width=8, fig.height=6}
nrow(dat_stations)

plots <- purrr::map(1:6, ~plot_closest(., dat_stations, dat_airports))
cowplot::plot_grid(plotlist = plots, nrow = 2)

plots <- purrr::map(7:11, ~plot_closest(., dat_stations, dat_airports))
cowplot::plot_grid(plotlist = plots, nrow = 2)

```

### c. Get closest airport (regardless of direction)
```{r}

df_distance_1 <- 1:nrow(dat_stations) %>%
  map_dfr(~get_closest(., dat_stations, dat_airports, n_closest = 1)
) 

```


### d. Get closest airport 'upstream'     
```{r}
#
# Go through one by one, 1-10:
# plot_closest(1, dat_stations, dat_airports, print_plot = TRUE) 
# For each, set 'pick_ustream' to the airport number (1-3) which is upstream

pick_upstream <- c(2,1,1,2,1,1,2,1,2,2,1)

# Put 'pick_upstream' into data frame for join, see below
df_upstream <- tibble(
  STATION_CODE = dat_stations$STATION_CODE,
  i = pick_upstream,
  Upstream = TRUE
)

# Get 3 closest stations
# Then add 'Upstream' column by joining 'df_upstream'
# Then filter using 'Upstream' column
df_distance_2 <- 1:nrow(dat_stations) %>%
  map_dfr(
    ~get_closest(
      ., dat_stations, dat_airports, n_closest = 3)
    ) %>%
  left_join(df_upstream) %>%
  filter(Upstream)


# check_distance_along_coast
```

### e. Combine  
```{r}

df1 <- df_distance_1 %>% 
  select(STATION_CODE, Distance, Airport) %>%
  rename(Distance1 = Distance, Airport1 = Airport)
df2 <- df_distance_2 %>% 
  select(STATION_CODE, Distance, Airport) %>%
  rename(Distance2 = Distance, Airport2 = Airport)

df_distance <- left_join(df1, df2)
  
  
```

### f. Add to data  
```{r}

dat3 <- dat2 %>%
  safe_left_join(df_distance, by = "STATION_CODE",
                 na_matches = "never", 
                   check = "bCV")

```


## 6. Plot all time series   
```{r}

params <- c("PFOS", "PFOSA", "PFBS", "PFDcA", "PFHxA", "PFHxS", 
          "PFHpA", "PFUdA", "PFOA", "PFNA", "PFUdA")

param <- "PFOS"

dat3 %>%
  filter(PARAM %in% param & TISSUE_NAME %in% "Lever") %>%
  arrange(Distance1) %>%
  mutate(Distance_f = 
           as.factor(paste0(STATION_CODE, " - ", round(Distance1, 1), " km")), 
         STATION_CODE = forcats::fct_inorder(Distance_f)) %>%
  ggplot(aes(MYEAR, VALUE_WW)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_log10() +
  facet_wrap(vars(STATION_CODE))

```


## 7. Test of analysis   

### Linear regression with station as factor, then new regression 
```{r}

param <- "PFOS"

df_regr <- dat3 %>%
  filter(PARAM %in% param & TISSUE_NAME %in% "Lever") 

mod0 <- lm(log(VALUE_WW) ~ MYEAR, data = df_regr)
mod1 <- lm(log(VALUE_WW) ~ MYEAR + STATION_CODE, data = df_regr)
anova(mod0, mod1)

# summary(mod)

df_estimates <- tibble(
  MYEAR = 2019,
  STATION_CODE = unique(df_regr$STATION_CODE)
)

pred <- predict(mod1, df_estimates, se.fit = TRUE)

df_estimates <- df_estimates %>%
  mutate(
    log_VALUE_WW = pred$fit,
    se = pred$se.fit
  ) %>%
  safe_left_join(df_distance, by = "STATION_CODE", 
                 na_matches = "never", 
                 check = "bCV")


ggplot(df_estimates, aes(Distance1, log_VALUE_WW)) +
  geom_point() +
  geom_text(aes(x = Distance1 + 1, label = STATION_CODE), hjust = 0) +
  geom_smooth(method = "lm") +
  labs(title = "Distance to closest airport")
ggplot(df_estimates, aes(Distance2, log_VALUE_WW)) +
  geom_point() +
  geom_text(aes(x = Distance2 + 1, label = STATION_CODE), hjust = 0) +
  geom_smooth(method = "lm") +
  labs(title = "Distance to closest 'upstream' airport")


```


## 8. Save data for analysis script  
```{r}

saveRDS(dat_stations, "Data/201_dat_stations.rds")
saveRDS(dat_airports, "Data/201_dat_airports.rds")
saveRDS(dat3, "Data/201_dat3.rds")
saveRDS(df_distance, "Data/201_df_distance.rds")



```

