---
title: "202_Airport_analysis"
author: "DHJ"
date: "8 9 2020"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    
---

## 1. Packages  
```{r, message=FALSE, results='hide', error=FALSE}

library(dplyr)
library(ggplot2)
library(purrr)
# devtools::install_github("moodymudskipper/safejoin")
library(safejoin)
library(leaflet)

library(knitr)    # for function kable()

source("202_Airport_analysis_functions.R")

options(width = 110) # 100 character with for tables etc.


```


## 2. Data  
PFOS PFOSA PFUnDA 
Ta med havner  
Gradient rød - grå - blå  eller lillatone for conc 2019  
PCA for log-transformert + fett + fiskelengde + år + stasjon    

### a1. Read data prepared in script 201   

```{r}

dat_stations <- readRDS("Data/201_dat_stations.rds")

# Metadata from script 103- contains distance along coast
# Coul also use Station_Name
meta_stations <- readRDS("Data/103_Selected_stations.rds") %>% # View()   
  filter(STATION_CODE %in% unique(dat_stations$STATION_CODE)) %>% 
  select(STATION_CODE, Station_Name, Dist_along_coast) %>%
  group_by(STATION_CODE) %>%
  summarise_all(first)

dat_airports <- readRDS("Data/201_dat_airports.rds")

# "Input_data/"
# dat <- readRDS("Input_data/109_adjusted_data_2020-08-05.rds") %>%
#   filter(MYEAR >= 1994)
dat <- readRDS("Data/201_dat3.rds") %>%
  filter(MYEAR >= 1994 & substr(PARAM, 1, 2) == "PF") %>%
  # Adding Station_Name:
  safe_left_join(meta_stations %>% select(-Dist_along_coast),
                 by = "STATION_CODE", na_matches = "never", check = "bCV")

station_order <- dat %>%
  distinct(STATION_CODE, Dist_along_coast) %>%
  arrange(Dist_along_coast) %>%
  pull(STATION_CODE)

stationname_order <- dat %>%
  distinct(Station_Name, Dist_along_coast) %>%
  arrange(Dist_along_coast) %>%
  pull(Station_Name)

# Set factors for STATION_CODE and Station_Name
dat <- dat %>%
  mutate(STATION_CODE = factor(STATION_CODE, levels = station_order)) %>%
  mutate(Station_Name = factor(Station_Name, levels = stationname_order))

         # Add 'Dist_along_coast'
df_distance <- readRDS("Data/201_df_distance.rds")%>%
  safe_left_join(meta_stations,
                 by = "STATION_CODE", na_matches = "never", check = "bCV")

# Map data

load("../../seksjon 318/Elveovervakning/Data_input/Norway_coastline_longlat2.RData")
map_norway_h <- norway_coast_longlat2


```

### a2 Tables
```{r, results='hold'}

tab <- dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005 & TISSUE_NAME %in% "Lever") %>%
  distinct(STATION_CODE, MYEAR, PARAM) %>%
  xtabs(~PARAM + MYEAR, .)

# flextable(tab)
knitr::kable(tab, caption = "Number of stations by substance/year (cod liver only)")

dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005) %>%
  distinct(STATION_CODE, MYEAR, SAMPLE_NO2) %>%
  xtabs(~STATION_CODE + MYEAR, .) %>%
  knitr::kable(
    caption = 
      "Sample size station/year ('B' stations = cod stations, the rest is blue mussel)")


if (FALSE){
  dat %>%
    filter(STATION_CODE %in% "24B" & MYEAR >= 2005) %>%
    xtabs(~PARAM + MYEAR, .)
}

```
### a3 Define parameters and their order  
Order:  
- First "PFOS", "PFOSA", "PFUdA" (most important)  
- Then acids from 6 carbons (PFHxA) to 10 carbons (PFDcA)  
- Then sulfonates: PFBS (4 carbons() and PFHxS (6 carbons)
```{r}

# rownames(tab) %>% dput()

# PFAS parameters
# rownames(tab) %>% dput()
# Order:


params <- c("PFOS", "PFOSA", "PFUdA", 
            "PFHxA", "PFHpA", "PFOA", "PFNA", "PFDcA", 
            "PFBS", "PFHxS")

params

```

### a4. Detection frequency    
Since 2005  
```{r, results='hold'}

dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005 & TISSUE_NAME %in% "Lever") %>%
  mutate(PARAM = factor(PARAM, levels = params)) %>%
  group_by(PARAM) %>%
  summarise(Percentage_detection = 100*mean(is.na(FLAG1)) %>% round(3), .groups = "drop") %>%
  kable(caption = "Percentage detection (cod liver only)" )

dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005 & TISSUE_NAME %in% "Lever") %>%
  mutate(PARAM = factor(PARAM, levels = params)) %>%
  group_by(PARAM, MYEAR) %>%
  summarise(Percentage_detection = 100*mean(is.na(FLAG1)) %>% round(3), .groups = "drop") %>%
  tidyr::pivot_wider(values_from = "Percentage_detection", names_from = "MYEAR")  %>%
  kable(caption = "Percentage detection per year (cod liver only)" )


```


### b. Map data
```{r 2b}

# MAp data (Norway w/o Svalbard + Jan Mayen)
test <- maps::map("world", "Norway", plot = FALSE)   # map data for Norway - this is just to get region names
sel <- grepl("Svalbard", test$names) | test$names == "Norway:Jan Mayen"  # select Svalbard + Jan Mayen
map <- maps::map("world", test$names[!sel], exact = TRUE, plot = FALSE)  # Norway w/o Svalbard + Jan Mayen
map_df <- data.frame(Longitude = map$x, Latitude = map$y)

#
# Add UTM coordinates (x and y) to map
#
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=33 +ellps=WGS84 +datum=WGS84 +units=m"

coordinate_exists <- !is.na(map_df$Longitude)   # sp doesn't like NAs
SP <- sp::SpatialPoints(map_df[coordinate_exists, c("Longitude", "Latitude")],
                    proj4string = sp::CRS(crs_longlat))
SP.UTM <- sp::spTransform(SP, sp::CRS(crs_utm))
# Add transformed coords to data set
map_df$x[coordinate_exists] <- SP.UTM@coords[,1]
map_df$y[coordinate_exists] <- SP.UTM@coords[,2]

cat("'map_df' created")

```

### c. Distance to airport        
**Distance1** = closest airport  
**Distance2** = closest 'upstream' airport (assuming Norwegian Coastal current going along the coast)  
**Dist_along_coast** = Distance along coast  
```{r}

df_distance %>% 
  mutate(Distance1 = round(Distance1, 1),
         Distance2 = round(Distance2, 1),
         Dist_along_coast = round(Dist_along_coast, 1)
         ) %>%
  select(-STATION_CODE) %>%
  select(Station_Name, everything()) %>%
  arrange(Dist_along_coast) %>%
  kable()



```

### d. Plot cod stations + airports    
```{r, fig.width=8, fig.height=6}

plots <- purrr::map(1:6, ~plot_closest(., dat_stations, dat_airports))
cowplot::plot_grid(plotlist = plots, nrow = 2)

plots <- purrr::map(7:11, ~plot_closest(., dat_stations, dat_airports))
cowplot::plot_grid(plotlist = plots, nrow = 2)

```

### e. Leaflet map  
```{r}

df <- dat %>%
  filter(PARAM %in% params & TISSUE_NAME %in% c("Lever", "Whole soft body")) %>% 
  distinct(STATION_CODE, TISSUE_NAME, Lon, Lat, MYEAR) %>%
  count(STATION_CODE, TISSUE_NAME, Lon, Lat)

icons_stations <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = case_when(
    df$TISSUE_NAME == "Whole soft body" ~ "orange",
    df$TISSUE_NAME == "Muskel" ~ "red")
)

icons_stations <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = case_when(
    df$TISSUE_NAME == "Whole soft body" ~ "orange",
    df$TISSUE_NAME == "Muskel" ~ "red")
)


leaflet(df) %>%
  addTiles() %>%
  addAwesomeMarkers(~Lon, ~Lat, icon = icons_stations,
                    label =  ~STATION_CODE) %>%
  addMarkers(~dat_airports$Lon, ~dat_airports$Lat,
             label = ~dat_airports$LUFTHAVN)

```

### f1. Plot cod liver PFAS time series    
Stations are arranged by distance to airport    
**Urban stations** are 30B Oslo (inner Oslofjord), 53B Bergen harbour and 43B2 Tromsø harbour  
```{r, fig.width = 9, fig.height=4}

for (param in params){
  
  gg <- dat %>%
    filter(PARAM %in% param & TISSUE_NAME %in% "Lever") %>%
    arrange(Distance1) %>%
    mutate(Distance_f = 
             as.factor(paste0(STATION_CODE, " - ", round(Distance1, 1), " km")), 
           STATION_CODE = forcats::fct_inorder(Distance_f),
           LOQ = case_when(
             !is.na(FLAG1) ~ "Under LOQ",  
             is.na(FLAG1) ~ "Over LOQ")
           ) %>%
    ggplot(aes(MYEAR, VALUE_WW)) +
    geom_point(aes(color = LOQ)) +
    geom_smooth(method = "lm", formula = 'y~x', se = FALSE) +
    scale_y_log10() +
    scale_x_continuous(breaks = seq(2005,2020,5), minor_breaks = 2005:2020) +
    scale_color_manual(values = c("black", "red2")) +
    facet_wrap(vars(STATION_CODE), nrow = 2) +
    theme_bw() +
    labs(title = param)
  
  print(gg)
}

```




### f2. Time trends of PFAS in cod liver        
Order = from Oslofjord (30B) to Tromsø (43B2)  
**Urban stations** are 30B Oslo (inner Oslofjord), 53B Bergen harbour and 43B2 Tromsø harbour  

```{r, message=FALSE, warning=FALSE, fig.width=9, fig.height=6}
library(broom)
get_reg_coef <- function(df) {
  lm <- lm(log_VALUE_WW ~ MYEAR, data = df)
  tidy(lm) %>%
    filter(term == "MYEAR") %>%
    mutate(PARAM = df$PARAM[1], 
           STATION_CODE = df$STATION_CODE[1],
           N_years = length(unique(df$MYEAR)))
}

results <- dat %>%
  filter(PARAM %in% params & TISSUE_NAME %in% "Lever") %>%
  mutate(log_VALUE_WW = log10(VALUE_WW),
         PARAM = factor(PARAM, levels = params)) %>%
  group_by(PARAM, STATION_CODE) %>%
  group_split() %>%
  map_df(~get_reg_coef(.))

results %>%
  select(PARAM, STATION_CODE, estimate) %>%
  mutate(estimate = round(estimate, 4)) %>%
  tidyr::pivot_wider(names_from = STATION_CODE, values_from = estimate) %>%
  kable(caption = "Slope of time regression (log10-transformed w.w. concentration)")

results %>%
  select(PARAM, STATION_CODE, p.value) %>%
  mutate(p.value = round(p.value, 4)) %>%
  tidyr::pivot_wider(names_from = STATION_CODE, values_from = p.value) %>%
  kable(caption = "P-value of time regression (log10-transformed w.w. concentration)")

results %>%
  filter(N_years >= 4) %>%
  ggplot(aes(STATION_CODE, estimate)) +
  geom_hline(aes(yintercept = 0)) +
  geom_pointrange(aes(ymin = estimate - 2*std.error, ymax = estimate + 2*std.error)) +
  facet_wrap(vars(PARAM)) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0)) +
  labs(title = "Slope of time regression (log10-transformed w.w. concentration)", 
       subtitle = "Range = conf.int. Only series of >= 4 years included")

```

### g. Plot PFASs against each other      
Stations are arranged by distance to airport  
```{r, fig.width = 9, fig.height=9}

df_wide <- dat %>%
  filter(PARAM %in% params & TISSUE_NAME %in% "Lever") %>%
  mutate(log_value = VALUE_WW) %>%
  select(PARAM, MYEAR, STATION_CODE, SAMPLE_NO2, log_value) %>%
  tidyr::pivot_wider(names_from = "PARAM", values_from = "log_value")

df_wide %>%
  select(-MYEAR, -SAMPLE_NO2, -STATION_CODE) %>%
  plot()

df_wide %>%
  select(-MYEAR, -SAMPLE_NO2, -STATION_CODE) %>%
  cor(use = "pairwise.complete.obs") %>%
  round(2) %>%
  kable(caption = "Correlation matrix (cod liver only)")

```


### h. Box plot  
```{r}

```


## 3. Analysis I - estimated concentration in 2019 {.tabset}     
Assuming that all time series are declining equally fast (on log scale) - see previous graphs   
Log wet weight concentration estimated for 2019   
**Urban stations** are 30B Oslo (inner Oslofjord), 53B Bergen harbour and 43B2 Tromsø harbour  


### a. Distance to closest airport   
```{r 3a, fig.width=6, fig.height=4}

# result <- get_estimates_parallel(param = "PFOS", dat, df_distance)

for (param in params){
  plot_estimates(param = param, dat, df_distance, 
                 analysis = "parallel",
                 distance_measure = "Distance1") %>%
    print()
  }
                                   

```

### b. Distance to closest 'upstream' airport     
```{r 3b, fig.width=6, fig.height=4}

# result <- get_estimates_parallel(param = "PFOS", dat, df_distance)

for (param in params){
  plot_estimates(param = param, dat, df_distance, 
                 analysis = "parallel",
                 distance_measure = "Distance2") %>%
    print()
  }
                                   

```


## 4. Analysis II - analysis of max measured concentration {.tabset}     
Regression assuming independent chance over time for each station  
Log w.w. concentration estimated for the year with highest concentration    
**Urban stations** are 30B Oslo (inner Oslofjord), 53B Bergen harbour and 43B2 Tromsø harbour  

### a. Estimates     
The red dot is Log w.w. concentration estimated for the year with highest concentration  
```{r 4a, fig.width = 9, fig.height=4}

for (param in params){
  
  result <- get_estimates_max(param = param, dat, df_distance)
  # result$anova
  
  gg <- dat %>%
    filter(PARAM %in% param & TISSUE_NAME %in% "Lever") %>%
    mutate(log_VALUE_WW = log10(VALUE_WW)) %>% # select(MYEAR, log_VALUE_WW, STATION_CODE)
    ggplot(aes(MYEAR, log_VALUE_WW)) +
    geom_point() +
    geom_smooth(method = "lm", formula = 'y ~ x', se = FALSE) +
    geom_point(data = result$estimates, color = "red2") +
    scale_x_continuous(breaks = seq(2005,2020,5), minor_breaks = 2005:2020) +
    facet_wrap(vars(STATION_CODE), nrow = 2) +
    theme_bw() +
    labs(title = param)
  print(gg)
  
}

```

### b. Closest airport     

```{r 4b, fig.width=6, fig.height=4}

for (param in params){
  plot_estimates(param = param, dat, df_distance, 
                 analysis = "max",
                 distance_measure = "Distance1") %>%
    print()
  }
                                   

```

### c. Closest 'upstream' airport     
```{r 4c, fig.width=6, fig.height=4}

# result <- get_estimates_parallel(param = "PFOS", dat, df_distance)

for (param in params){
  plot_estimates(param = param, dat, df_distance, 
                 analysis = "max",
                 distance_measure = "Distance2") %>%
    print()
  }
                                   

```


### d. Distance along coast       
```{r 4d, fig.width=6, fig.height=4}

# result <- get_estimates_parallel(param = "PFOS", dat, df_distance)

for (param in params){
  plot_estimates(param = param, dat, df_distance, 
                 analysis = "max",
                 distance_measure = "Dist_along_coast") %>%
    print()
  }
                                   

```

### e. Coast distance + Upstream airport  
```{r, fig.width=8, fig.height=4}

# result <- get_estimates_parallel(param = "PFOS", dat, df_distance)

for (param in params){
  plot_estimates(param = param, dat, df_distance, 
                 analysis = "max",
                 distance_measure = "Dist_along_coast_Dist2")
  }
                                   
```

## 5. Boxplots  
Note:   
- 2009 were lacking for 2009 data were lacking for 13B and 15B, where we used 2007 (13B) and 2007-08 (15B)  
- For PFUdA there is no 2009 data (or perhaps they are in the database, if I dig a little?).  
    - So we use 2012-2014 vs 2018-19 for PFUdA   
- Stations are ordered following their position along the coast (that can be changed)    
- EQS added for PFOS. No EQS for PFOSA (PFOA has EQS = 91)
```{r, fig.width=8, fig.height=6}

plot1 <- function(param, data){
  data %>%
    filter(PARAM %in% param & TISSUE_NAME %in% "Lever") %>%
    mutate(Year = case_when(
      STATION_CODE %in% "13B" & MYEAR %in% 2007 ~ "2009",
      STATION_CODE %in% "15B" & MYEAR %in% 2006:2007 ~ "2009",
      MYEAR %in% 2009 ~ "2009",
      MYEAR %in% 2019 ~ "2019",
      TRUE ~ as.character(NA))
    ) %>%
    filter(!is.na(Year)) %>%
    ggplot(aes(Station_Name, VALUE_WW)) +
    geom_boxplot(aes(fill = Year), position = position_dodge2(preserve = "single")) +
    theme(axis.text.x = element_text(angle = -30, hjust = 0)) +
    labs(title = param,
         caption = "Note: 2009 data were lacking for 13B and 15B, where we used 2007 (13B) and 2007-08 (15B)")
}

plot2 <- function(param, data){
  data %>%
    filter(PARAM %in% param & TISSUE_NAME %in% "Lever") %>%
    mutate(Year = case_when(
      MYEAR %in% 2012:2014 ~ "2012-2014",
      MYEAR %in% 2018:2019 ~ "2018-2019",
      TRUE ~ as.character(NA))
    ) %>%
    filter(!is.na(Year)) %>%
    ggplot(aes(Station_Name, VALUE_WW)) +
    geom_boxplot(aes(fill = Year), position = position_dodge2(preserve = "single")) +
    scale_fill_brewer(palette = "Set3") +
    theme(axis.text.x = element_text(angle = -30, hjust = 0)) +
    labs(title = param)
}

gg1 <- plot1("PFOS", data = dat)
gg2 <- plot1("PFOSA", data = dat)
gg3 <- plot2("PFUdA", data = dat)
# gg1 
# gg2
# gg3
gg1 + 
  geom_hline(aes(yintercept = 9.1), color = "red2", linetype = 2) +
  scale_y_log10(sec.axis = sec_axis(~ ., breaks = 9.1, labels = function(x) "EQS")) +
  theme(axis.text.y.right = element_text(color = "red2", size = rel(1.5)))

gg2 + scale_y_log10()
gg3 + scale_y_log10()

```

## 6. Map   

```{r, fig.width=6, fig.height=7}

for (param in c("PFOS", "PFOSA", "PFUdA")){
  
  df <- dat %>%
    filter(PARAM %in% param & TISSUE_NAME %in% "Lever" & MYEAR == 2019 & !is.na(VALUE_WW)) %>%
    group_by(STATION_CODE, Lon, Lat) %>%
    summarise(`Concentration 2019` = median(VALUE_WW), .groups = "drop") %>%
    mutate(textside = case_when(
      STATION_CODE %in% c("30B", "36B", "13B", "53B") ~ "right",
      TRUE ~ "left"
    ))
  gg <- ggplot(df) +
    annotation_map(map_norway_h, aes(long, lat), fill = terrain.colors(10)[7]) +
    geom_point(aes(Lon, Lat, fill = `Concentration 2019`), pch = 21, size = rel(3)) +
    geom_text(data = subset(df, textside == "right"),
              aes(Lon, Lat, label = STATION_CODE), hjust = -0.4, size = rel(3)) +
    geom_text(data = subset(df, textside == "left"),
              aes(Lon, Lat, label = STATION_CODE), hjust = 1.4, size = rel(3)) +
    scale_fill_distiller(palette = "PRGn") +
    annotate("text", x = -8, y = 71.5, label = param, hjust = 0, size = rel(5)) +
    coord_map("lambert", parameters = c(64, 12), xlim = c(-1,30), ylim = c(57, 72)) +
    theme_bw() +
    theme(axis.title = element_blank(),
        legend.position = c(.68, .15))
    
    print(gg)

}

```


## 7. PCA      

### Make data ready
```{r, results = 'hold'}

dat_wide <- dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005 & TISSUE_NAME %in% "Lever") %>%
  select(STATION_CODE, Dist_along_coast, MYEAR, SAMPLE_NO2, PARAM, VALUE_WW) %>%
  mutate(log_VALUE_WW = log10(VALUE_WW)) %>%
  select(-VALUE_WW) %>%
  tidyr::pivot_wider(names_from = "PARAM", values_from = "log_VALUE_WW")# %>%
  #as.data.frame()  # for setting row names

# rownames(dat_wide) <- with(dat_wide,
#                            paste(STATION_CODE, MYEAR, SAMPLE_NO2))
  
df <- dat_wide %>% 
  select(-c(STATION_CODE, Dist_along_coast, MYEAR, SAMPLE_NO2))
n_param <- apply(!is.na(df), 1, sum)
cat("Number of parameters per sample: \n")
table(n_param)

cat("\n")
cat("Number of samples per parameter: \n")
n_samples <- apply(!is.na(df), 2, sum)
n_samples

```

## 8. PCA excluding PFDcA, PFHxS, PFUdA - LOQ values kept  {.tabset}  

### Perform PCA
```{r}

complete_cases_1 <- dat_wide %>% 
  select(PFBS, PFHpA, PFHxA, PFNA, PFOA, PFOS) %>%
  complete.cases()

cat("Original data have", nrow(dat_wide), "rows \n")
dat_wide_1 <- dat_wide %>% 
  filter(complete_cases_1)
cat("Data for analysis (all parameters present) have", nrow(dat_wide_1), "rows \n\n")
  
dat_wide_1 %>%
  select(PFBS, PFHpA, PFHxA, PFNA, PFOA, PFOS) %>%
  scale() %>%            # scale to 0 mean and unit variance
  prcomp() ->            # do PCA
  pca                    # store result as `pca`

# now display the results from the PCA analysis
pca

# Principal components  
pca_data <- data.frame(pca$x, 
                       STATION_CODE = dat_wide_1$STATION_CODE, 
                       MYEAR = dat_wide_1$MYEAR,
                       Dist_along_coast = dat_wide_1$Dist_along_coast)

```


### Percent variance explained  
```{r}
percent <- 100*pca$sdev^2 / sum(pca$sdev^2)
kable(
  tibble(
    PC = paste0("PC", seq_along(percent)), 
    Percent = round(percent, 1))
)

```

### Plot PCs by year  
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = MYEAR)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_distiller(palette = "RdYlBu") +
  theme_bw()

```

### Plot PCs by year, medians  
```{r}
df <- pca_data %>%
  group_by(MYEAR) %>%
  summarise_at(vars(PC1,PC2,PC3), median)

ggplot(df, aes(x = PC1, y = PC2, fill = MYEAR)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = MYEAR), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC1), ylim = range(df$PC2)) +
  theme_bw()

```


### Plot PCs by station, PC1 vs PC2    
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = STATION_CODE)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_brewer(palette = "RdYlBu") +
  theme_bw()

```

### Plot PCs by station, PC2 vs PC3    
```{r}

ggplot(pca_data, aes(x = PC2, y = PC3, fill = STATION_CODE)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_brewer(palette = "RdYlBu") +
  theme_bw()

```


### Plot PCs by distance along coast, PC1 vs PC2    
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = Dist_along_coast)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_distiller(palette = "RdYlBu") +
  theme_bw()

```

### Plot PCs by station / distance along coast, PC1 + PC2  
```{r}

df <- pca_data %>%
  group_by(STATION_CODE, Dist_along_coast) %>%
  summarise_at(vars(PC1,PC2,PC3), median)

ggplot(df, aes(x = PC1, y = PC2, fill = Dist_along_coast)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = STATION_CODE), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC1), ylim = range(df$PC2)) +
  theme_bw()



```


### Plot PCs by station / distance along coast, PC2 + PC3  
```{r}

ggplot(df, aes(x = PC2, y = PC3, fill = Dist_along_coast)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = STATION_CODE), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC2), ylim = range(df$PC3)) +
  theme_bw()


```



### Rotation matrix  
```{r}

# capture the rotation matrix in a data frame
rotation_data <- data.frame(
  pca$rotation, 
  Parameter = row.names(pca$rotation)
)

# define a pleasing arrow style
arrow_style <- arrow(
  length = unit(0.05, "inches"),
  type = "closed"
)

# now plot, using geom_segment() for arrows and geom_text() for labels
ggplot(rotation_data) + 
  geom_segment(aes(xend = PC1, yend = PC2), x = 0, y = 0, arrow = arrow_style) + 
  geom_text(aes(x = PC1, y = PC2, label = Parameter), hjust = 0, size = 3, color = "red4") + 
  xlim(-1., 1.25) + 
  ylim(-1., 1.) +
  coord_fixed() + # fix aspect ratio to 1:1
  theme_bw()

ggplot(rotation_data) + 
  geom_segment(aes(xend = PC2, yend = PC3), x = 0, y = 0, arrow = arrow_style) + 
  geom_text(aes(x = PC2, y = PC3, label = Parameter), hjust = 0, size = 3, color = "red4") + 
  xlim(-1., 1.25) + 
  ylim(-1., 1.) +
  coord_fixed() + # fix aspect ratio to 1:1
  theme_bw()

```


## 9. PCA excluding PFDcA, PFHxS, PFUdA - LOQ values replaced {.tabset}       
Values under LOQ have been replaced by random values bewteen LOQ/2 and LOQ.  

### Perform PCA
```{r}

dat_wide <- dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005 & TISSUE_NAME %in% "Lever") %>% 
  add_random_data() %>%
  select(STATION_CODE, Dist_along_coast, MYEAR, SAMPLE_NO2, PARAM, VALUE_WW_r) %>%
  mutate(log_VALUE_WW = log10(VALUE_WW_r)) %>%
  select(-VALUE_WW_r) %>%
  tidyr::pivot_wider(names_from = "PARAM", values_from = "log_VALUE_WW")# %>%

complete_cases_1 <- dat_wide %>% 
  select(PFBS, PFHpA, PFHxA, PFNA, PFOA, PFOS) %>%
  complete.cases()

cat("\n")
cat("Original data have", nrow(dat_wide), "rows \n")
dat_wide_1 <- dat_wide %>% 
  filter(complete_cases_1)
cat("Data for analysis (all parameters present) have", nrow(dat_wide_1), "rows \n\n")

dat_wide_1 %>%
  select(PFBS, PFHpA, PFHxA, PFNA, PFOA, PFOS) %>%
  scale() %>%            # scale to 0 mean and unit variance
  prcomp() ->            # do PCA
  pca                    # store result as `pca`

# now display the results from the PCA analysis
pca

# Principal components
pca_data <- data.frame(pca$x, 
                       STATION_CODE = dat_wide_1$STATION_CODE, 
                       MYEAR = dat_wide_1$MYEAR,
                       Dist_along_coast = dat_wide_1$Dist_along_coast)

```


### Percent variance explained  
```{r}
percent <- 100*pca$sdev^2 / sum(pca$sdev^2)
kable(
  tibble(
    PC = paste0("PC", seq_along(percent)), 
    Percent = round(percent, 1))
)

```

### Plot PCs by year  
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = MYEAR)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_distiller(palette = "RdYlBu") +
  theme_bw()

```

### Plot PCs by year, medians  
```{r}
df <- pca_data %>%
  group_by(MYEAR) %>%
  summarise_at(vars(PC1,PC2,PC3), median)

ggplot(df, aes(x = PC1, y = PC2, fill = MYEAR)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = MYEAR), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC1), ylim = range(df$PC2)) +
  theme_bw()


```


### Plot PCs by station, PC1 vs PC2    
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = STATION_CODE)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_brewer(palette = "RdYlBu") +
  theme_bw()

```

### Plot PCs by station, PC2 vs PC3    
```{r}

ggplot(pca_data, aes(x = PC2, y = PC3, fill = STATION_CODE)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_brewer(palette = "RdYlBu") +
  theme_bw()

```


### Plot PCs by distance along coast, PC1 vs PC2    
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = Dist_along_coast)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_distiller(palette = "RdYlBu") +
  theme_bw()

```


### Plot PCs by station / distance along coast, PC1 + PC2  
```{r}

df <- pca_data %>%
  group_by(STATION_CODE, Dist_along_coast) %>%
  summarise_at(vars(PC1,PC2,PC3), median)

ggplot(df, aes(x = PC1, y = PC2, fill = Dist_along_coast)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = STATION_CODE), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC1), ylim = range(df$PC2)) +
  theme_bw()



```


### Plot PCs by station / distance along coast, PC2 + PC3  
```{r}

ggplot(df, aes(x = PC2, y = PC3, fill = Dist_along_coast)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = STATION_CODE), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC2), ylim = range(df$PC3)) +
  theme_bw()


```


### Rotation matrix  
```{r}

# capture the rotation matrix in a data frame
rotation_data <- data.frame(
  pca$rotation, 
  Parameter = row.names(pca$rotation)
)

# define a pleasing arrow style
arrow_style <- arrow(
  length = unit(0.05, "inches"),
  type = "closed"
)

# now plot, using geom_segment() for arrows and geom_text() for labels
ggplot(rotation_data) + 
  geom_segment(aes(xend = PC1, yend = PC2), x = 0, y = 0, arrow = arrow_style) + 
  geom_text(aes(x = PC1, y = PC2, label = Parameter), hjust = 0, size = 3, color = "red4") + 
  xlim(-1., 1.25) + 
  ylim(-1., 1.) +
  coord_fixed() + # fix aspect ratio to 1:1
  theme_bw()

ggplot(rotation_data) + 
  geom_segment(aes(xend = PC2, yend = PC3), x = 0, y = 0, arrow = arrow_style) + 
  geom_text(aes(x = PC2, y = PC3, label = Parameter), hjust = 0, size = 3, color = "red4") + 
  xlim(-1., 1.25) + 
  ylim(-1., 1.) +
  coord_fixed() + # fix aspect ratio to 1:1
  theme_bw()

```


## 10. PCS including PFDcA, PFHxS, PFUdA - LOQ values replaced {.tabset}     
Values under LOQ have been replaced by random values bewteen LOQ/2 and LOQ.  

### Perform PCA  
```{r}

dat_wide <- dat %>%
  filter(substr(PARAM, 1, 2) == "PF" & MYEAR >= 2005 & TISSUE_NAME %in% "Lever") %>% 
  add_random_data() %>%
  select(STATION_CODE, Dist_along_coast, MYEAR, SAMPLE_NO2, PARAM, VALUE_WW_r) %>%
  mutate(log_VALUE_WW = log10(VALUE_WW_r)) %>%
  select(-VALUE_WW_r) %>%
  tidyr::pivot_wider(names_from = "PARAM", values_from = "log_VALUE_WW")# %>%

complete_cases_1 <- dat_wide %>% 
  select(PFBS, PFHpA, PFHxA, PFNA, PFOA, PFOS, PFDcA, PFHxS, PFUdA) %>%
  complete.cases()

cat("\n")
cat("Original data have", nrow(dat_wide), "rows \n")
dat_wide_1 <- dat_wide %>% 
  filter(complete_cases_1)
cat("Data for analysis (all parameters present) have", nrow(dat_wide_1), "rows \n\n")

dat_wide_1 %>%
  select(PFBS, PFHpA, PFHxA, PFNA, PFOA, PFOS, PFDcA, PFHxS, PFUdA) %>%
  scale() %>%            # scale to 0 mean and unit variance
  prcomp() ->            # do PCA
  pca                    # store result as `pca`

# now display the results from the PCA analysis
pca


# Principal components  
pca_data <- data.frame(pca$x, 
                       STATION_CODE = dat_wide_1$STATION_CODE, 
                       MYEAR = dat_wide_1$MYEAR,
                       Dist_along_coast = dat_wide_1$Dist_along_coast)

```


### Percent variance explained  
```{r}
percent <- 100*pca$sdev^2 / sum(pca$sdev^2)
kable(
  tibble(
    PC = paste0("PC", seq_along(percent)), 
    Percent = round(percent, 1))
)

```

### Plot PCs by year  
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = MYEAR)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_distiller(palette = "RdYlBu") +
  theme_bw()

```

### Plot PCs by year, medians  
```{r}
df <- pca_data %>%
  group_by(MYEAR) %>%
  summarise_at(vars(PC1,PC2,PC3), median)

ggplot(df, aes(x = PC1, y = PC2, fill = MYEAR)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = MYEAR), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC1), ylim = range(df$PC2)) +
  theme_bw()

```


### Plot PCs by station, PC1 vs PC2    
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = STATION_CODE)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_brewer(palette = "RdYlBu") +
  theme_bw()

```

### Plot PCs by station, PC2 vs PC3    
```{r}

ggplot(pca_data, aes(x = PC2, y = PC3, fill = STATION_CODE)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_brewer(palette = "RdYlBu") +
  theme_bw()

```


### Plot PCs by distance along coast, PC1 vs PC2    
```{r}

ggplot(pca_data, aes(x = PC1, y = PC2, fill = Dist_along_coast)) + 
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  scale_fill_distiller(palette = "RdYlBu") +
  theme_bw()

```

### Plot PCs by station / distance along coast, PC1 + PC2  
```{r}

df <- pca_data %>%
  group_by(STATION_CODE, Dist_along_coast) %>%
  summarise_at(vars(PC1,PC2,PC3), median)

ggplot(df, aes(x = PC1, y = PC2, fill = Dist_along_coast)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = STATION_CODE), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC1), ylim = range(df$PC2)) +
  theme_bw()



```


### Plot PCs by station / distance along coast, PC2 + PC3  
```{r}

ggplot(df, aes(x = PC2, y = PC3, fill = Dist_along_coast)) + 
  geom_path() +
  geom_point(shape = 21, size = rel(2.5), alpha = 0.5) +
  geom_text(aes(label = STATION_CODE), hjust = -0.3) +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = rangex(df$PC2), ylim = range(df$PC3)) +
  theme_bw()


```


### Rotation matrix  
```{r}

# capture the rotation matrix in a data frame
rotation_data <- data.frame(
  pca$rotation, 
  Parameter = row.names(pca$rotation)
)

# define a pleasing arrow style
arrow_style <- arrow(
  length = unit(0.05, "inches"),
  type = "closed"
)

# now plot, using geom_segment() for arrows and geom_text() for labels
ggplot(rotation_data) + 
  geom_segment(aes(xend = PC1, yend = PC2), x = 0, y = 0, arrow = arrow_style) + 
  geom_text(aes(x = PC1, y = PC2, label = Parameter), hjust = 0, size = 3, color = "red4") + 
  xlim(-1., 1.25) + 
  ylim(-1., 1.) +
  coord_fixed() + # fix aspect ratio to 1:1
  theme_bw()

ggplot(rotation_data) + 
  geom_segment(aes(xend = PC2, yend = PC3), x = 0, y = 0, arrow = arrow_style) + 
  geom_text(aes(x = PC2, y = PC3, label = Parameter), hjust = 0, size = 3, color = "red4") + 
  xlim(-1., 1.25) + 
  ylim(-1., 1.) +
  coord_fixed() + # fix aspect ratio to 1:1
  theme_bw()

```